---
title: "Exploration"
author: "Evan Canfield"
date: "7/30/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Purpose
Currently it does not appear that you can feed a dataframe with a Simple Features column into any of the Parallel package functions, on windows. These Simple Features columns are generated in the pre=processing steps, which themselves are parallel. Therefore, this notebook will explore creating a parallel process for identifying parallel segments, but the pre-processing steps will not be parallel.

# Import
## Packages
```{r import_packages}
if (!require(pacman)) {install.packages("pacman")}
pacman::p_load(
  glue,
  parallel,
  tidyverse
)

# Import custom functions
r_files <- list.files(
  path = "./../R/", pattern = "*.R", full.names = TRUE, 
  recursive = FALSE, include.dirs = FALSE
  )
for (file in r_files) {
  source(file)
}

# Set randomized seed
set.seed(5590)
```

## Data
### Street Map
```{r import_data}
file_dir <- "./../data"
file_name <- "network_02_no_parallel_seperation_complete_2021-08-24.RDS"
file_path <- file.path(file_dir, file_name)
network_raw.df <- readr::read_rds(file_path)
print(file_path)
```

### Extract OSM Query Date
```{r extract_api_query_date}
date_regex <- "\\d{4}-\\d{2}-\\d{2}"
osm_query_date <- stringr::str_extract(file_name, date_regex)
print(osm_query_date)
```

# Subset
```{r subset_network}
SUBSET_NETWORK <- TRUE

if (SUBSET_NETWORK) {
  # Define subsetting Parameters
  center_lat <- 35.242974
  center_lon <- -80.794735
  radius     <- 1e3

  # Execute
  network.df <- subset_lat_lon(
    network    = network_raw.df, 
    lat_center = center_lat, 
    lon_center = center_lon,
    radius     = radius 
    )
  
} else{
  network.df <- network_raw.df
}

n_edge_sub <- length(network.df$edge_id)
n_edge_total <- length(network_raw.df$edge_id)
per_total <- round(100*(1 - ((n_edge_total - n_edge_sub)/n_edge_total)),1)

# Print output
print(glue::glue("Subset Network:\t\t{SUBSET_NETWORK}"))
if (SUBSET_NETWORK){
  print(glue::glue("Percent of Network:\t{per_total}%"))
}
```

# Test Parallel / Non-Parllel Tags
## Normal / Orthogonal
### Parallel
```{r}
# start_time <- Sys.time()
# x <- networkLinestringProcessing(
#   network_raw.df, 
#   parallel = TRUE,
#   start_time = NA,
#   k = 6,
#   verbose = 2
# )
# 
# time_elapsed <- secondsToPeriodTime(start_time)
# print(glue::glue("Time Elapsed: {time_elapsed}"))
```

### Non - Parallel
```{r}
# start_time <- Sys.time()
# y <- networkLinestringProcessing(
#   network_raw.df, 
#   parallel = FALSE,
#   start_time = NA,
#   k = 6,
#   verbose = 2
# )
# 
# time_elapsed <- secondsToPeriodTime(start_time)
# print(glue::glue("Time Elapsed: {time_elapsed}"))
```

## Complete Network
### Parallel
```{r}
# start_time <- Sys.time()
# network_par <- networkLinestringProcessingComplete(
#   network_raw.df, 
#   parallel = TRUE,
#   start_time = NA,
#   k = 6,
#   verbose = 2
# )
# 
# time_elapsed <- secondsToPeriodTime(start_time)
# print(glue::glue("Time Elapsed: {time_elapsed}"))
```

### Non - Parallel
```{r}
# start_time <- Sys.time()
# network_non_par <- networkLinestringProcessingComplete(
#   network_raw.df, 
#   parallel = FALSE,
#   start_time = NA,
#   k = 6,
#   verbose = 2
# )
# 
# time_elapsed <- secondsToPeriodTime(start_time)
# print(glue::glue("Time Elapsed: {time_elapsed}"))
```


# identifyParallelSegmentsClusterLabel
## Function Inputs
```{r}
k <- 6
start_time <- Sys.time()
verbose <- 2

print(glue::glue("Function inputs defined."))
```
## Assign Cluster Numbers
```{r}
# Assign cluster number
network.list <- networkClusters(network.df, k)
cluster_labels <- names(network.list)
network_w_cluster.df <- dplyr::bind_rows(network.list)
```

## Execute Function
```{r}
identifyParallelSegmentsCluster(
  cluster_label     = 1,
  network_w_cluster = network_w_cluster.df,
  start_time        = NA, 
  verbose           = 1 
) 
```

# Implement Parallel Methods
## Set up Cluster
```{r}
# Define dataset variables and required sub-functions for export to cluster
cluster_data <- c("network.list", "k")
cluster_functions <- c(
  "exportParallelEdgeResults", "preProcessingParallelIdentification", 
  "makeLinestring", "makeLinestringVector", "networkClusters",
  "secondsToPeriodTime", "compareParallelEdges", 
  "networkLinestringProcessing", "lineStringLength", "subset_lat_lon", 
  "line_length"
)
cluster_variables <- c(cluster_data, cluster_functions)

# Create Cluster
cl <- parallel::makeCluster(k)

# Export required variables to cluster
parallel::clusterExport(
  cl      = cl, 
  varlist = cluster_variables, 
  envir   = environment()
)

print(glue::glue("Cluster created and values exported."))
```

## Run Parallel Action
```{r}
# Execute parallel implementation of segment labeling
network.mtx <- parallel::parSapply(
  cl               = cl, 
  X                = cluster_labels, 
  FUN              = identifyParallelSegmentsCluster,
  network          = network_w_cluster.df,
  start_time       = start_time,
  verbose          = verbose
)

# Convert each matrix column to dataframe and store in list
network_compile.list <- vector(mode = "list", length = k)

for (i in seq(1,k,1)){
  network_compile.list[[i]] <- dplyr::as_tibble(network.mtx[,i])
}

# Bind all subset network dataframes in the list
network <- bind_rows(network_compile.list)

# Remove cluster label
network <- network %>% select(-.cluster)

network %>% 
  arrange(desc(n_parallel_segments))
```

## Function
```{r}
identifyParallelSegmentsPar(
  network    = network.df, 
  k          = 6, 
  start_time = NA, 
  verbose    = verbose
)
```

