---
title: "Exploration"
author: "Evan Canfield"
date: "7/30/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Purpose
Currently it does not appear that you can feed a dataframe with a Simple Features column into any of the Parallel package functions, on windows. These Simple Features columns are generated in the pre=processing steps, which themselves are parallel. Therefore, this notebook will explore creating a parallel process for identifying parallel segments, but the pre-processing steps will not be parallel.

# Import
## Packages
```{r import_packages}
if (!require(pacman)) {install.packages("pacman")}
pacman::p_load(
  glue,
  parallel,
  tidyverse
)

# Import custom functions
r_files <- list.files(
  path = "./../R/", pattern = "*.R", full.names = TRUE, 
  recursive = FALSE, include.dirs = FALSE
  )
for (file in r_files) {
  source(file)
}

# Set randomized seed
set.seed(5590)
```

## Data
### Street Map
```{r import_data}
file_dir <- "./../data"
file_name <- "network_02_no_parallel_seperation_complete_2021-08-24.RDS"
file_path <- file.path(file_dir, file_name)
network_raw.df <- readr::read_rds(file_path)
print(file_path)
```

### Extract OSM Query Date
```{r extract_api_query_date}
date_regex <- "\\d{4}-\\d{2}-\\d{2}"
osm_query_date <- stringr::str_extract(file_name, date_regex)
print(osm_query_date)
```

# Subset
```{r subset_network}
SUBSET_NETWORK <- TRUE

if (SUBSET_NETWORK) {
  # Define subsetting Parameters
  center_lat <- 35.242974
  center_lon <- -80.794735
  radius     <- 3e3

  # Execute
  network.df <- subset_lat_lon(
    network    = network_raw.df, 
    lat_center = center_lat, 
    lon_center = center_lon,
    radius     = radius 
    )
  
} else{
  network.df <- network_raw.df
}

n_edge_sub <- length(network.df$edge_id)
n_edge_total <- length(network_raw.df$edge_id)
per_total <- round(100*(1 - ((n_edge_total - n_edge_sub)/n_edge_total)),1)

# Print output
print(glue::glue("Subset Network:\t\t{SUBSET_NETWORK}"))
if (SUBSET_NETWORK){
  print(glue::glue("Percent of Network:\t{per_total}%"))
}
```

# Test Parallel / Non-Parllel Tags
## Normal / Orthogonal
### Parallel
```{r}
# start_time <- Sys.time()
# x <- networkLinestringProcessing(
#   network_raw.df, 
#   parallel = TRUE,
#   start_time = NA,
#   k = 6,
#   verbose = 2
# )
# 
# time_elapsed <- secondsToPeriodTime(start_time)
# print(glue::glue("Time Elapsed: {time_elapsed}"))
```

### Non - Parallel
```{r}
# start_time <- Sys.time()
# y <- networkLinestringProcessing(
#   network_raw.df, 
#   parallel = FALSE,
#   start_time = NA,
#   k = 6,
#   verbose = 2
# )
# 
# time_elapsed <- secondsToPeriodTime(start_time)
# print(glue::glue("Time Elapsed: {time_elapsed}"))
```

## Complete Network
### Parallel
```{r}
# start_time <- Sys.time()
# network_par <- networkLinestringProcessingComplete(
#   network_raw.df, 
#   parallel = TRUE,
#   start_time = NA,
#   k = 6,
#   verbose = 2
# )
# 
# time_elapsed <- secondsToPeriodTime(start_time)
# print(glue::glue("Time Elapsed: {time_elapsed}"))
```

### Non - Parallel
```{r}
# start_time <- Sys.time()
# network_non_par <- networkLinestringProcessingComplete(
#   network_raw.df, 
#   parallel = FALSE,
#   start_time = NA,
#   k = 6,
#   verbose = 2
# )
# 
# time_elapsed <- secondsToPeriodTime(start_time)
# print(glue::glue("Time Elapsed: {time_elapsed}"))
```

# identifyParallelSegmentsClusterLabel
## Function Inputs
```{r}
k <- 6
start_time <- Sys.time()
verbose <- 2

print(glue::glue("Function inputs defined."))
```

## Assign Cluster Numbers
```{r}
# Assign cluster number
network.list <- networkClusters(network.df, k)
cluster_labels <- names(network.list)
network_w_cluster.df <- dplyr::bind_rows(network.list)
```

## Execute Function
```{r}
identifyParallelSegmentsCluster(
  cluster_label     = 1,
  network_w_cluster = network_w_cluster.df,
  start_time        = NA, 
  verbose           = 2 
) 
```

# Determine Best Method to Subset Comparison Network
## Filter Cluster Subset Comparison Data by Bounding Box Limits
**TO DO**: Test with colored network visuals for each step
 * Full network
 * Select cluster
 * Lat/lon reduction
  * To set distance, find distance between center lat lon and any of the corners. This should be the max distance for the radius subset. 
  * Add a buffer/safety zone around it
  * Buffer should just be the distance threshold for st_within_dist
 * St_witihin_distance box
 
 
### Process Network
```{r}
network_norm_orth <- networkLinestringProcessing(
  network_w_cluster.df,
  parallel = FALSE
)

network_norm <- network_norm_orth[['normal']]
```

#### Plot
```{r}
p <- plotStreets(network_w_cluster.df, ".cluster")
plotly::ggplotly(p)
```

### Determine Bounding Box
```{r}
cluster_label <- network_w_cluster.df %>% 
  dplyr::slice_sample(n = 1) %>% 
  dplyr::pull(.cluster) 

network_norm_cluster <- network_norm %>% 
  dplyr::filter(.cluster == cluster_label)

sf_geo_cluster<- network_norm_cluster %>% dplyr::pull(geometry)

geom_bbox <- sf::st_bbox(sf_geo_cluster)
```

#### Plot
```{r}
network_norm_cluster_id <- network_norm %>% 
  mutate(highlight = if_else(.cluster == cluster_label, "a", "b")
         )
p <- plotStreets(network_norm_cluster_id, "highlight")
plotly::ggplotly(p)
```

### Subset by Latitude / Longitude
#### Determine Longest Distance
```{r}
lon_center <- mean(c(geom_bbox[1] , geom_bbox[3]))
lat_center <- mean(c(geom_bbox[2], geom_bbox[4]))

bbox_corner_to_center <- sqrt((lon_center - geom_bbox[1])^2 + (lat_center - geom_bbox[2])^2)
```

#### Determine Subsetted Network (Lat/Lon)
```{r}
print(glue::glue("Number of rows - compare - pre:\t\t{length(network_w_cluster.df$edge_id)}"))
print(glue::glue("Number of rows - cluster:\t\t{length(network_norm_cluster$edge_id)}"))

deg_to_m_conv <- 1.11e5
dist_adj_factor <- 1.2
  
network_compare_lat_lon <- subset_lat_lon(
  network = network_norm, 
  lat_center = lat_center, 
  lon_center = lon_center, 
  radius = (bbox_corner_to_center * dist_adj_factor * deg_to_m_conv)
  )

print(glue::glue("Number of rows - compare - post:\t{length(network_compare_lat_lon$edge_id)}"))
```
#### Plot
##### Lat/Lon Subset Area
```{r}
edge_cluster <- network_norm_cluster %>% pull(edge_id)
edge_lat_lon <- network_compare_lat_lon %>% pull(edge_id)
# edge_within <- network_compare_within %>% pull(edge_id)

network_norm_w_highlight <- network_norm %>% 
  mutate(
    highlight = case_when(
      # edge_id %in% edge_cluster ~ "a",
      # edge_id %in% edge_within ~ "b",
      edge_id %in% edge_lat_lon ~ "c",
      TRUE ~ "d"
    )
  )

p <- plotStreets(network_norm_w_highlight, "highlight")
plotly::ggplotly(p)
```

##### Cluster and Lat/Lon Subset Area
```{r}
edge_cluster <- network_norm_cluster %>% pull(edge_id)
edge_lat_lon <- network_compare_lat_lon %>% pull(edge_id)
# edge_within <- network_compare_within %>% pull(edge_id)

network_norm_w_highlight <- network_norm %>% 
  mutate(
    highlight = case_when(
      edge_id %in% edge_cluster ~ "a",
      # edge_id %in% edge_within ~ "b",
      edge_id %in% edge_lat_lon ~ "c",
      TRUE ~ "d"
    )
  )

p <- plotStreets(network_norm_w_highlight, "highlight")
plotly::ggplotly(p)
```

### Determine Subsetted Network - st_within
```{r}
network_compare_within <- cropComparisonNetwork(
  network_cluster  = network_norm_cluster,
  network_complete = network_compare_lat_lon,
  dist             = 150,
  verbose          = 0
  )

print(glue::glue("Number of rows - subset - within:\t{length(network_compare_within$edge_id)}"))
```

### Plot Different Network Subsetting methods
```{r}
edge_cluster <- network_norm_cluster %>% pull(edge_id)
edge_within <- network_compare_within %>% pull(edge_id)
edge_lat_lon <- network_compare_lat_lon %>% pull(edge_id)


network_norm_w_highlight <- network_norm %>% 
  mutate(
    highlight = case_when(
      edge_id %in% edge_cluster ~ "a",
      edge_id %in% edge_within ~ "b",
      edge_id %in% edge_lat_lon ~ "c",
      TRUE ~ "d"
    )
  )

p <- plotStreets(network_norm_w_highlight, "highlight")

plotly::ggplotly(p)
```

```{r}
print(glue::glue("Number of rows - compare - pre:\t\t{length(network_w_cluster.df$edge_id)}"))
print(glue::glue("Number of rows - cluster:\t\t{length(network_norm_cluster$edge_id)}"))

network_compare_lat_lon <- subset_lat_lon(
  network = network_norm, 
  lat_center = lat_center, 
  lon_center = 
  lon_center, 
  radius = 4e3 * 1.1 
  )

print(glue::glue("Number of rows - compare - post:\t{length(network_compare_lat_lon$edge_id)}"))

edge_id_cluster <- network_norm_cluster$edge_id
edge_id_compare <- network_compare_lat_lon$edge_id

test <- all(edge_id_cluster %in% edge_id_compare)
print(glue::glue("All custer edges in compare network:\t{test}"))
```

```{r}
network_sf_geo <- network_compare_lat_lon %>% pull(geometry)
cluster_sf_geo <- network_norm_cluster %>% pull(geometry)
dist <- 100

edge_to_edge_test <- sf::st_is_within_distance(
  x      = network_sf_geo, 
  y      = cluster_sf_geo, 
  sparse = FALSE,
  dist   = dist
)

  
  # Determine number of network edges
n_edges_network <- dim(edge_to_edge_test)[1]
  
keep_edge <- apply(
  X      = edge_to_edge_test, 
  MARGIN = 1, 
  FUN    = any
)

print(glue::glue("Number of edges to keep:\t\t{sum(keep_edge)}"))

network_compare_lat_lon$keep <- keep_edge

edge_id_compare_2 <- network_compare_lat_lon %>% 
  filter(keep) %>% 
  pull()

edge_id_cluster %in% edge_id_compare_2
```


```{r}
# network_norm_orth <- networkLinestringProcessing(
#   network_w_cluster.df, 
#   parallel = FALSE
# )
# 
# # Extract complete network
# network_complete <- network_norm_orth[['normal']]
# 
# # Reduce to cluster
# cluster_label <- 1
# network <- network_complete %>% 
#   dplyr::filter(.cluster == cluster_label)
```

### Filter Comparison Dataframe
```{r}
# # Extract simple feature geometries
# cluster_sf_geo <- network %>% dplyr::pull(geometry)
# network_sf_geo <- network_complete %>% dplyr::pull(geometry)
# 
# # Determine which edges in the complete network are within x distance of the cluster
# # Allows for reduction in size of comparison network
# edge_to_edge_test <- sf::st_is_within_distance(
#   network_sf_geo,
#   cluster_sf_geo, 
#   sparse = FALSE,
#   dist = 100
#   )
# 
# # Determine number of network edges
# n_edges_network <- dim(edge_to_edge_test)[1]
# 
# # If any edge in the network is within x distance of any edge in the 
# # cluster subset, select True.
# keep_edge <- apply(
#   X      = edge_to_edge_test, 
#   MARGIN = 1, 
#   FUN    = any
#   )
# 
# # Assign output vector to comparison network dataframe
# network_complete$near_cluster <- keep_edge
# 
# # reduce to only edges within x distance from any cluster edge
# network_complete_crop <- network_complete %>% 
#   dplyr::filter(near_cluster)
# 
# network_complete_crop
```

```{r}
# cropComparisonNetwork <- function(network, network_complete, dist = 100) {
#   # Extract simple feature geometries
#   cluster_sf_geo <- network %>% dplyr::pull(geometry)
#   network_sf_geo <- network_complete %>% dplyr::pull(geometry)
#   
#   # Determine which edges in the complete network are within x distance of the cluster
#   # Allows for reduction in size of comparison network
#   edge_to_edge_test <- sf::st_is_within_distance(
#     x      = network_sf_geo, 
#     y      = cluster_sf_geo, 
#     sparse = FALSE,
#     dist   = dist
#     )
# 
#   # Determine number of network edges
#   n_edges_network <- dim(edge_to_edge_test)[1]
#   
#   # If any edge in the network is within x distance of any edge in the 
#   # cluster subset, select True.
#   keep_edge <- apply(
#     X      = edge_to_edge_test, 
#     MARGIN = 1, 
#     FUN    = any
#     )
# 
#   # Assign output vector to comparison network dataframe
#   network_complete$near_cluster <- keep_edge
#   
#   # reduce to only edges within x distance from any cluster edge
#   network_complete %>% 
#     dplyr::filter(near_cluster)
# }
# 
# cropComparisonNetwork(network, network_complete)
```


# Implement Parallel Methods
## Set up Cluster
```{r}
# Define dataset variables and required sub-functions for export to cluster
cluster_data <- c("network.list", "k")
cluster_functions <- c(
  "exportParallelEdgeResults", "preProcessingParallelIdentification", 
  "makeLinestring", "makeLinestringVector", "networkClusters",
  "secondsToPeriodTime", "compareParallelEdges", 
  "networkLinestringProcessing", "lineStringLength", "subset_lat_lon", 
  "line_length", "cropComparisonNetwork"
)
cluster_variables <- c(cluster_data, cluster_functions)

# Create Cluster
cl <- parallel::makeCluster(k)

# Export required variables to cluster
parallel::clusterExport(
  cl      = cl, 
  varlist = cluster_variables, 
  envir   = environment()
)

print(glue::glue("Cluster created and values exported."))
```

## Run Parallel Action
```{r}
# Execute parallel implementation of segment labeling
network.mtx <- parallel::parSapply(
  cl               = cl, 
  X                = cluster_labels, 
  FUN              = identifyParallelSegmentsCluster,
  network          = network_w_cluster.df,
  start_time       = start_time,
  verbose          = verbose
)

# Convert each matrix column to dataframe and store in list
network_compile.list <- vector(mode = "list", length = k)

for (i in seq(1,k,1)){
  network_compile.list[[i]] <- dplyr::as_tibble(network.mtx[,i])
}

# Bind all subset network dataframes in the list
network <- bind_rows(network_compile.list)

# Remove cluster label
network <- network %>% select(-.cluster)

network %>% 
  arrange(desc(n_parallel_segments))
```

## Function
```{r}
identifyParallelSegmentsPar(
  network      = network.df %>% dplyr::slice_sample(prop = 0.5), 
  k            = 6, 
  start_time   = NA, 
  verbose      = 1,
  log_progress = TRUE
)
```