---
title: "Exploration"
author: "Evan Canfield"
date: "7/30/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Purpose
Determine how to ensure roads represented as two parallel lines have the same segment intersections on both sides of the line.

# Import
## Packages
```{r import_packages}
if (!require(pacman)) {install.packages("pacman")}
pacman::p_load(
  glue,
  parallel,
  sf,
  stringi,
  tidyverse
)

# Import custom functions
r_files <- list.files(
  path = "./../R/", pattern = "*.R", full.names = TRUE, 
  recursive = FALSE, include.dirs = FALSE
  )
for (file in r_files) {
  source(file)
}

# Set randomized seed
set.seed(5590)
```

## Data
### Street Map
```{r import_data}
file_dir <- "./../data"
file_name <- "network_02_no_parallel_seperation_complete_2021-08-24.RDS"
file_path <- file.path(file_dir, file_name)
network_raw.df <- readr::read_rds(file_path)
print(file_path)
```

### Extract OSM Query Date
```{r extract_api_query_date}
date_regex <- "\\d{4}-\\d{2}-\\d{2}"
osm_query_date <- stringr::str_extract(file_name, date_regex)
print(osm_query_date)
```

### Segment Map
```{r}
file_name <- glue::glue("segment_mapping_no_parallel_seperation_{osm_query_date}.RDS")
file_path <- file.path(file_dir, file_name)
segment_map <- read_rds(file_path)
print(file_path)
```

# Subset
```{r subset_network}
SUBSET_NETWORK <- TRUE

if (SUBSET_NETWORK) {
  # Define subsetting Parameters
  center_lat <- 35.242974
  center_lon <- -80.794735
  radius     <- 1e3

  # Execute
  network.df <- subset_lat_lon(
    network    = network_raw.df, 
    lat_center = center_lat, 
    lon_center = center_lon,
    radius     = radius 
    )
  
} else{
  network.df <- network_raw.df
}

n_edge_sub <- length(network.df$edge_id)
n_edge_total <- length(network_raw.df$edge_id)
per_total <- round(100*(1 - ((n_edge_total - n_edge_sub)/n_edge_total)),1)

# Print output
print(glue::glue("Subset Network:\t\t{SUBSET_NETWORK}"))
if (SUBSET_NETWORK){
  print(glue::glue("Percent of Network:\t{per_total}%"))
}
```

# identifyParallelSegments - Not Parallel
## Function Inputs
```{r}
start_time <- Sys.time()
verbose <- 2
network <- network.df
network_complete <- network

# Determine cluster count
core_factor <- 0.75
k <- trunc(parallel::detectCores() * core_factor)
print(glue::glue("Number of Cores: {k}"))
```

## Function - Pre-process datasets
```{r}
# x <- networkLinestringProcessing(
#   network          = network.df, 
#   network_complete = network.df,
#   start_time       = NA,
#   k                = 6,
#   verbose          = 2
#   )
```

## Function - Identify Parallel Segmsents - Not Parallel
```{r}
# y <- identifyParallelSegments(
#   network          = network_raw.df,
#   k                = 8,
#   start_time       = NA,
#   verbose          = 1,
#   network_complete = NA
# )
# 
# print(glue::glue("identifyParallelSegments Executed"))
```

# identifyParallelSegments - Parallel
## Process Normal / Orthogonal Networks
```{r}
network_norm_orth <- networkLinestringProcessing(
  network          = network.df,
  start_time       = start_time,
  k                = k,
  verbose          = verbose
)
```

## Define Complete Network
```{r}
network_complete <- network_norm_orth[["normal"]]
```

## Assign Clusters Labels
```{r}
# Assign to Network
network.list <- networkClusters(network_norm_orth[["normal"]], k)

# Apply Same Cluster Labels to Orthogonal
## Bind Normal network
network_w_cluster.df <- dplyr::bind_rows(network.list)

## Join Cluster labels
network_orth_w_cluster.df <- network_norm_orth[["orthogonal"]] %>% 
  dplyr::left_join(
    network_w_cluster.df %>% select(edge_id, .cluster), 
    by = "edge_id"
  ) %>% 
  dplyr::select(.cluster, dplyr::everything())

norm_orth_cluster_networks.list <- vector(mode = "list", length = length(network.list)) 
names(norm_orth_cluster_networks.list) <- names(network.list)

for (cluster_label in names(network.list)){
  # Initialize temporary named list
  tmp.list <- vector(mode = "list", length = 2)
  names(tmp.list) <- c("normal", "orthogonal")
  
  # Subset networks by cluster label and assign to temporary list
  tmp.list[["normal"]] <- network_w_cluster.df %>% 
    filter(
      .cluster == cluster_label 
    ) %>% 
    arrange(edge_id)
  
  tmp.list[["orthogonal"]] <- network_orth_w_cluster.df %>% 
    filter(
      .cluster == cluster_label 
    ) %>% 
    arrange(edge_id)
  
  
  # Assign temporary list to output list
  norm_orth_cluster_networks.list[[cluster_label]] <- tmp.list
}
```

## Parallel Test
### MCAPPLY
```{r}
start_time <- Sys.time()

network_norm_orth <- networkLinestringProcessing(
  network          = network.df,
  start_time       = start_time,
  k                = k,
  verbose          = 0
)

network_complete <- network_norm_orth[["normal"]]

# Assign to Network
network.list <- networkClusters(network_norm_orth[["normal"]], k)

# Apply Same Cluster Labels to Orthogonal
## Bind Normal network
network_w_cluster.df <- dplyr::bind_rows(network.list)

## Join Cluster labels
network_orth_w_cluster.df <- network_norm_orth[["orthogonal"]] %>% 
  dplyr::left_join(
    network_w_cluster.df %>% select(edge_id, .cluster), 
    by = "edge_id"
  ) %>% 
  dplyr::select(.cluster, dplyr::everything())

norm_orth_cluster_networks.list <- vector(mode = "list", length = length(network.list)) 
names(norm_orth_cluster_networks.list) <- names(network.list)

for (cluster_label in names(network.list)){
  # Initialize temporary named list
  tmp.list <- vector(mode = "list", length = 2)
  names(tmp.list) <- c("normal", "orthogonal")
  
  # Subset networks by cluster label and assign to temporary list
  tmp.list[["normal"]] <- network_w_cluster.df %>% 
    filter(
      .cluster == cluster_label 
    ) %>% 
    arrange(edge_id)
  
  tmp.list[["orthogonal"]] <- network_orth_w_cluster.df %>% 
    filter(
      .cluster == cluster_label 
    ) %>% 
    arrange(edge_id)
  
  
  # Assign temporary list to output list
  norm_orth_cluster_networks.list[[cluster_label]] <- tmp.list
}

network_w_parallel.list <- parallel::mclapply(
  X                = norm_orth_cluster_networks.list, 
  FUN              = compareParallelEdgesListWrapper,
  network_complete = network_complete,
  verbose          = 0
  )

network <- dplyr::bind_rows(network_w_parallel.list)

time_elapsed <- secondsToPeriodTime(start_time)
print(glue::glue("Time Elapsed - Parallel: {time_elapsed}"))
```

### Non - Parallel
```{r}
start_time <- Sys.time()

y <- identifyParallelSegments(
  network          = network.df,
  k                = k,
  start_time       = NA,
  verbose          = 0,
  network_complete = NA
)

time_elapsed <- secondsToPeriodTime(start_time)
print(glue::glue("Time Elapsed - Parallel: {time_elapsed}"))
```


## Process Complete Network
```{r}
  network_complete <- networkLinestringProcessing(
    network          = network.df,
    start_time       = start_time,
    k                = k,
    verbose          = verbose
  )
```

## Set up Cluster
```{r}
# Define dataset variables and required sub-functions for export to cluster
cluster_data <- c("network.list", "k")
cluser_functions <- c(
  "exportParallelEdgeResults", "identifyParallelSegments", "preProcessingParallelIdentification", 
  "makeLinestring", "makeLinestringVector","makeLinestringVectorPar", "networkClusters", 
  "secondsToPeriodTime", "compareParallelEdges"
  )
cluster_variables <- c(cluster_data, cluser_functions)

# Create Cluster
cl <- parallel::makeCluster(k)

# Export required variables to cluster
parallel::clusterExport(
  cl      = cl, 
  varlist = cluster_variables, 
  envir   = environment()
)

print(glue::glue("Cluster created and values exported."))
```


## Run Function
```{r}
# Execute parallel implementation of segment labeling
network.mtx <- parallel::parSapply(
  cl               = cl, 
  X                = norm_orth_cluster_networks.list, 
  FUN              = compareParallelEdgesListWrapper,
  network_complete = network_complete,
  k                = k,
  start_time       = start_time,
  verbose          = verbose
)

network.mtx

# Convert each matrix column to dataframe and store in list
network_compile.list <- vector(mode = "list", length = k)
for (i in seq(1,k,1)){
  network_compile.list[[i]] <- as.data.frame(network.mtx[,i])
}

# Bind all subset network dataframes in the list
network <- bind_rows(network_compile.list)

# Remove cluster label
network <- network %>% select(-.cluster)

network
```