---
title: "Generate Network - Segments Applied - Pre-Parallel Seperation"
author: "Evan Canfield"
date: "7/30/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Purpose
The purpose of this notebook is to test a random walk structure for labeling segments which uses a more efficient, directional approach, rather than a purely random walk approach.

# Import
## Packages
```{r import_packages}
if (!require(pacman)) {install.packages("pacman")}
pacman::p_load(
  glue,
  lubridate,
  parallel,
  sf,
  stringi,
  tidyverse
)

# Import custom functions
r_files <- list.files("./../R/", full.names = TRUE)
for (file in r_files) {
  source(file)
}

# Set randomized seed
set.seed(5590)
```

## Data
### Street Map
```{r import_data}
file_dir <- "./../data"
file_name <- "network_01_dodgr_2021-08-24.RDS"
file_path <- file.path(file_dir, file_name)
network_raw.df <- readr::read_rds(file_path)
```

# Subset
```{r}
SUBSET_NETWORK <- TRUE

if (SUBSET_NETWORK) {
  # Define subsetting Parameters
  center_lat <- 35.242974
  center_lon <- -80.794735
  radius <- 1e4

  # Execute
  network.df <- subset_lat_lon(
    network    = network_raw.df, 
    lat_center = center_lat, 
    lon_center = center_lon,
    radius     = radius 
    )
} else{
  network.df <- network_raw.df
}

```

# Walk - Step by Step Work
## Before Function Actions
### Define Segment ID Columns > Empty
```{r}
network.df$segment_id <- NA_character_
```

## Inside Function - Pre Walk Setup
### Determine Number of NA values in Segment ID Column
```{r}
# Extract all segment ids
utilized_segment_ids <- purrr::discard(network.df$segment_id, is.na)

n_na_segments <- length(network.df$segment_id) - length(utilized_segment_ids)
print(glue::glue("Number of Total Observations:\t{length(network.df$segment_id)}"))
print(glue::glue("Number of NA Segment IDs:\t{n_na_segments}"))
```

### Import / Define Datasets
#### Intersection Nodes
```{r}
file_dir <- "./../data"
file_name <- "intersection_nodes_2021-08-24.RDS"
file_path <- file.path(file_dir, file_name)
intersection_nodes <- readr::read_rds(file_path)
```

#### Dead End Nodes
```{r}
# Define Dead-End Nodes
dead_end_nodes <- bind_rows(
  network.df %>% select(from_id) %>% rename(id = from_id),
  network.df %>% select(to_id) %>% rename(id = to_id)
  ) %>% 
  count(id) %>% 
  filter(n == 1) %>% 
  pull(id)

print(glue::glue("Number of Dead End Nodes:\t{length(dead_end_nodes)}"))
```

#### Parallel Separation Nodes
```{r}
file_dir <- "./../data"
file_name <- "parallel_separation_nodes_2021-08-24.RDS"
file_path <- file.path(file_dir, file_name)
if (file.exists(file_path)) {
  
  print("File Found")
  parallel_separation_nodes <- readr::read_rds(file_path)
  
} else{
  print("File Node Found")
  parallel_separation_nodes <- vector(mode = "character", length = 0)
}
```

#### Create Vector of Nodes to Stop Walk
```{r}
halt_walk_nodes_init <- c(intersection_nodes, parallel_separation_nodes, dead_end_nodes)
```


## Inside Function - Inside While Loop - Outside Recursive Walk
### Select Random Edge ID Without Segment
```{r}
starting_edge <- network.df %>% 
  dplyr::slice_sample(n=1) %>% 
  pull(edge_id)

print(glue::glue("Edge ID:\t{starting_edge}"))
```

### Initialize Edge Id List
```{r}
edges_in_segment <- vector(mode = "character", length = 0)
```

## Inside Function- Inside While Loop - Inside Recursive Loop
### Pass Through the following Information
```{r}
edge_iter <- starting_edge
edges_in_segment <- edges_in_segment
halt_walk_nodes <- halt_walk_nodes_init
direction <- "to"
```

### Add Edge to Edges List
```{r}
edges_in_segment <- c(edges_in_segment, edge_iter)

edges_in_segment
```

```{r}
network.df %>% 
    filter(edge_id == edge_iter)
```

### Select Node To Inspect
```{r}
if (direction == "to"){
  node_iter <- network.df %>% 
    filter(edge_id == edge_iter) %>% 
    pull(to_id)
  
} else {
    node_iter <- network.df %>% 
    filter(edge_id == edge_iter) %>% 
    pull(from_id)
}

print(glue::glue("Direction:\t{direction}"))
print(glue::glue("Selected Node:\t{node_iter}"))
```

### Node Check
```{r}
# Intersection
bool_stop <- node_iter %in% halt_walk_nodes

print(glue::glue("Stop Walk:\t{bool_stop}"))
```

### If Stop Walk = False
#### Append Current Node to Stop List
```{r}
halt_walk_nodes <- c(halt_walk_nodes,node_iter)
```

#### Determine Other Edge Where Node Is Used
```{r}
if (direction == "to"){
  edge_iter <- network.df %>% 
    filter(from_id == node_iter) %>% 
    pull(edge_id)
  
} else {
  edge_iter <- network.df %>% 
    filter(to_id == node_iter) %>% 
    pull(edge_id)
}
print(glue::glue("Direction:\t{direction}"))
print(glue::glue("Selected Node:\t{edge_iter}"))
```

#### Pass Into Recursive Function
```{r}
edge_iter <- edge_iter
edges_in_segment <- edges_in_segment
halt_walk_nodes <- halt_walk_nodes
direction <- "to"
```

### If Stop Walk = True
#### Return vector of edge_ids 
```{r}
edges_in_segment
```

## Inside Function- Inside While Loop - After Recursive Loop
### Generate Segment ID
```{r}
segment_id_rdm <- randomID(utilized_segment_ids)
print(glue::glue("Segment ID:\t{segment_id_rdm}"))
```

### Apply Segment ID to Edges in Vector
```{r}
edges_in_segment <- unique(edges_in_segment)

network.df <- network.df %>% 
  mutate(
    segment_id = if_else(
      condition = (edge_id %in% edges_in_segment),
      true =  segment_id_rdm, 
      false = NA_character_
    )
  )
```

### Calculate Number of Missing Segment Ids
```{r}
# Extract all segment ids
utilized_segment_ids <- purrr::discard(network.df$segment_id, is.na)

n_na_segments <- length(network.df$segment_id) - length(utilized_segment_ids)
print(glue::glue("Number of Total Observations:\t{length(network.df$segment_id)}"))
print(glue::glue("Number of NA Segment IDs:\t{n_na_segments}"))
```

## Inside Function - After While Loop
```{r}
# return network dataframe
```


# Define Functions
## Walk
```{r}
walkSegment <- function(
  network,
  edge,
  edges_in_segment,
  halt_walk_nodes,
  direction,
  verbose = 0
) {
  # Add edge to vector of edges within segment
  edges_in_segment <- c(edges_in_segment, edge)
  
  # Select Node to walk to 
  if (direction == "to"){
    node <- network %>% 
      filter(edge_id == edge) %>% 
      pull(to_id)
    } else {
      node <- network %>% 
        dplyr::filter(edge_id == edge) %>% 
        dplyr::pull(from_id)
    }
  
  if (verbose >= 3) {
    print(glue::glue("Direction:\t\t\t{direction}"))
    print(glue::glue("Selected Node:\t\t\t{node}"))
  }
  
  # Check if walk should be halted
  HALT_WALK <- node %in% halt_walk_nodes
  
  if (verbose >= 3) {
    print(glue::glue("Halt Walk:\t\t\t{HALT_WALK}"))
  }

    # Recursive choice - act on whether walk should stop
  if (HALT_WALK){
    
    edges_in_segment
    
  } else {
    
    # Add node to halt walk nodes. This is to prevent getting trapped in a 
    # loop, like a track or closed-loop walking path.
    halt_walk_nodes <- c(halt_walk_nodes, node)
    
    
    # Select next edge
    if (direction == "to"){
      
      next_edge <- network %>% 
        dplyr::filter(from_id == node) %>% 
        dplyr::pull(edge_id)
      
    } else {
      
      next_edge <- network %>% 
        dplyr::filter(to_id == node) %>% 
        dplyr::pull(edge_id)
      
    }
    
    if (verbose >= 3) {
      print(glue::glue("Edge ID - Next:\t\t\t{next_edge}"))
    }
    
    # Verify that next_edge is a single length vector. If it is not, there is an error in the 
    # properly defining the halt nodes
    if (length(next_edge) > 1 ) {
      msg1 <- glue::glue("Next edge selected does not have length of one.")
      msg2 <- glue::glue("Next Edge Length:\t{length(next_edge)}")
      msg3 <- glue::glue("Current Edge:\t{edge}")
      msg4 <- glue::glue("Problem Node:\t{node}")
      stop_msg <- glue::glue("{msg1}\n{msg2}\n{msg3}\n{msg4}")
      stop(stop_msg)
      
    }
    
    # Walk to next edge
    walkSegment(
      network          = network,
      edge             = next_edge,
      edges_in_segment = edges_in_segment,
      halt_walk_nodes  = halt_walk_nodes,
      direction        = direction,
      verbose          = verbose
      ) 
    
  }
}
```

## Struture
```{r}
labelSegments <- function(network, verbose = 0){
  start_time <- Sys.time()
  
  # SETUP######################################################################
  # Load Intersection Nodes
  file_dir <- "./../data"
  file_name <- "intersection_nodes_2021-08-24.RDS"
  file_path <- file.path(file_dir, file_name)
  intersection_nodes <- readr::read_rds(file_path)
  
   # Load Parallel Separation Nodes
  file_name <- "parallel_separation_nodes_2021-08-24.RDS"
  file_path <- file.path(file_dir, file_name)
  if (file.exists(file_path)) {
    parallel_separation_nodes <- readr::read_rds(file_path)
    
    if (verbose >= 1){
      print(glue::glue("Parallel Separation File Node:\tFound"))
    }
    
  } else{
    # Initialize Empty Vector
    parallel_separation_nodes <- vector(mode = "character", length = 0)
    
    if (verbose >= 1){
      print(glue::glue("Parallel Separation File:\tNot Found"))
    }
  }
  
  # Define Dead End Nodes
  ## Defined, not loaded, because depenging on if the street network is
  ## the complete network or just a subset will determine change which
  ## nodes are dead ends
  dead_end_nodes <- dplyr::bind_rows(
    network %>% dplyr::select(from_id) %>% dplyr::rename(id = from_id),
    network %>% dplyr::select(to_id) %>% dplyr::rename(id = to_id)
    ) %>% 
    dplyr::count(id) %>% 
    dplyr::filter(n == 1) %>% 
    dplyr::pull(id)
  
  if (verbose >= 1){
    print(glue::glue("Number of Dead End Nodes:\t{length(dead_end_nodes)}"))
  }
  
  # Create compiled vector of nodes that will stop the walking function
  halt_walk_nodes_init <- c(
    intersection_nodes, parallel_separation_nodes, dead_end_nodes
    )
  
  # Determine previously used segment ids and the number of cases
  # where segment ID is NA
  # Determine status of segment ids used, how many edge ids have been 
  # assigned a segment id, and how many edges still require a segment id.
  total_obs <- length(network$edge_id)
  utilized_segment_ids <- unique(purrr::discard(network$segment_id, is.na))
  n_segment_ids <- length(utilized_segment_ids)
  n_edges_labeled <- sum(!is.na(network$segment_id))
  n_edges_unlabeled <- total_obs - n_edges_labeled
    
    if (verbose >= 2){
      m0 <- glue::glue("--------------------------------------------------")
      m1 <- glue::glue("Status Counts:")
      m2 <- glue::glue("Total Observations:\t\t{total_obs}")
      m3 <- glue::glue("Unique Segment IDs:\t\t{n_segment_ids}")
      m4 <- glue::glue("Edges w/ a Segment ID:\t\t{n_edges_labeled}")
      m5 <- glue::glue("Edges w/o a Segment ID:\t\t{n_edges_unlabeled}")
      print(glue::glue("{m0}\n{m1}\n{m2}\n{m3}\n{m4}\n{m5}\n{m0}"))
    }
  
  # Iteration Loop ############################################################
  # Initialize loop counter
  n <- 1
  while (n_edges_unlabeled > 0){
    if (verbose >= 2){
      print(glue::glue("_____________________ NEW LOOP _____________________"))
    }
    
    # Set Up Walk -------------------------------------------------------------
    # Select starting point edge
    starting_edge <- network %>% 
      filter(is.na(segment_id)) %>% 
      dplyr::slice_sample(n=1) %>% 
      dplyr::pull(edge_id)

    if (verbose >= 2){
      print(glue::glue("Edge ID - Start:\t\t{starting_edge}"))
    }
    # Initialize vector to capture all edges within a single segment
    edges_in_segment <- vector(mode = "character", length = 0)
    
    # Start Walk - To Direction -----------------------------------------------
    edges_in_segment<- walkSegment(
      network = network,
      edge = starting_edge,
      edges_in_segment = edges_in_segment,
      halt_walk_nodes = halt_walk_nodes_init,
      direction = "to",
      verbose = verbose
    )
    
    # Start Walk - From Direction ---------------------------------------------
    edges_in_segment<- walkSegment(
      network = network,
      edge = starting_edge,
      edges_in_segment = edges_in_segment,
      halt_walk_nodes = halt_walk_nodes_init,
      direction = "from",
      verbose = verbose
    )
    
    # Update Network Table ---------------------------------------------------
    ## Generate Random Segment ID
    segment_id_rdm <- randomID(unique(utilized_segment_ids))
    
    if (verbose >= 2){
      print(glue::glue("Segment ID:\t\t\t{segment_id_rdm}"))
    }
    
    ## Reduce to unique values in case of double counting
    edges_in_segment <- unique(edges_in_segment)
    
    ## Label edges in network table with segment id
    network <- network %>% 
      mutate(
        segment_id = dplyr::if_else(
          condition = (edge_id %in% edges_in_segment),
          true =  segment_id_rdm, 
          false = segment_id
        )
      )
    
    # Recalculate while loop parameters ---------------------------------------
    # Determine previously used segment ids and the number of cases
    # where segment ID is NA
    # Determine status of segment ids used, how many edge ids have been 
    # assigned a segment id, and how many edges still require a segment id.
    utilized_segment_ids <- unique(purrr::discard(network$segment_id, is.na))
    n_segment_ids <- length(utilized_segment_ids)
    n_edges_labeled <- sum(!is.na(network$segment_id))
    n_edges_unlabeled <- total_obs - n_edges_labeled
      
      if (verbose >= 2){
        m0 <- glue::glue("--------------------------------------------------")
        m1 <- glue::glue("Status Counts:")
        m2 <- glue::glue("Total Observations:\t\t{total_obs}")
        m3 <- glue::glue("Unique Segment IDs:\t\t{n_segment_ids}")
        m4 <- glue::glue("Edges w/ a Segment ID:\t\t{n_edges_labeled}")
        m5 <- glue::glue("Edges w/o a Segment ID:\t\t{n_edges_unlabeled}")
        print(glue::glue("{m0}\n{m1}\n{m2}\n{m3}\n{m4}\n{m5}\n{m0}"))
      }
    
    # Print Updates -----------------------------------------------------------
    if ((n %% 1e2 == 0) & verbose >= 1) {
      end_time <- Sys.time()
      elapsed_time <- secondsToPeriodTime(start_time, end_time)
      print(glue::glue("Elapsed Time:\t\t\t{elapsed_time}"))
      
      percent_rem <- round(100 * (total_obs - n_edges_unlabeled)/total_obs,1)
      print(glue::glue("Percent Edges Remaining:\t{percent_rem}%"))
    }
    
    # Safety Valve -----------------------------------------------------------
    if ((n > 1e5) & verbose >= 1){
      stop(glue::glue("Maximum iterations reached:\t{n}"))
    }
    
    n <- n + 1
    
  }
  
  if (verbose >= 1){
    m0 <- glue::glue("--------------------------------------------------")
    m1 <- glue::glue("Status Counts:")
    m2 <- glue::glue("Total Observations:\t\t{total_obs}")
    m3 <- glue::glue("Unique Segment IDs:\t\t{n_segment_ids}")
    m4 <- glue::glue("Edges w/ a Segment ID:\t\t{n_edges_labeled}")
    m5 <- glue::glue("Edges w/o a Segment ID:\t\t{n_edges_unlabeled}")
    print(glue::glue("{m0}\n{m1}\n{m2}\n{m3}\n{m4}\n{m5}\n{m0}"))
    }
  
  network
}


```

# Test
## Generate Segment Labels
```{r}
network.df$segment_id <- NA_character_
network_w_segments.df <- labelSegments(network.df, verbose = 1)

network_w_segments.df
```

## Plot
```{r}
highlight <- "segment_id"

p <- plotStreets(df = network_2.df, color_feature = highlight)

plotly::ggplotly(p)
```

