---
title: "Exploration"
author: "Evan Canfield"
date: "7/30/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Purpose
Determine how to ensure roads represented as two parallel lines have the same segment intersections on both sides of the line.

# Import
## Packages
```{r import_packages}
if (!require(pacman)) {install.packages("pacman")}
pacman::p_load(
  glue,
  sf,
  stringi,
  tidyverse
)

# Import custom functions
r_files <- list.files("./../R/", full.names = TRUE)
for (file in r_files) {
  source(file)
}

# Set randomized seed
set.seed(5590)
```

## Data
### Street Map
```{r import_data}
# Street network data.frame
network_raw.df <- readRDS("./../data/dodgr_network_charlotte_nc_2021-03-17.RDS")

# Define column type to avoid messages
col_type <- c(
  "edge_id" = "character",
  "to_id" = "character",
  "from_id" = "character",
  "status" = "character"
)
```

# Processing
## Drop Duplicates
* There are duplicate rows, with from and to ids swapped
```{r}
# Record number of observations before dropping
n_edge_raw <- length(network_raw.df$edge_id)

# Drop duplicate observations
network.df <- network_raw.df %>% 
    mutate(
    dup_id = if_else(
      from_id > to_id, 
      paste(to_id, from_id, sep = "_"),
      paste(from_id, to_id,  sep = "_")
    )
  )  %>% 
  group_by(dup_id) %>% 
  filter(row_number()==1) %>% 
  ungroup() %>% 
  select(-dup_id)

# Record number of observations after dropping
n_edge_post <- length(network.df$edge_id)

glue('Number of observations - original:\t\t\t{n_edge_raw}')
glue('Number of observations - post duplicate removal:\t{n_edge_post}')
```

### Spot Check
```{r}
network.df %>% 
  filter(
    edge_id %in% seq(213042, 213052, 1)
  )
```

### Highway Types
```{r}
network.df %>% 
  count(highway) %>% 
  arrange(desc(n))
```

### Remove Street Types
```{r}
street_types <- c('path', 'primary_link', 'secondary_link', 'tertiary_link', 'trunk_link', 
                  'living_street')
network.df <- network.df %>% 
  filter(!(highway %in% street_types))
```


# Determine Intersections
* Each **edge_id** is defined by two nodes, and TO and FROM node. 
* If a node is used by multiple edge_ids as a TO or FROM node then we know this node is an intersection.
* A case to be careful of is when a node is used only twice, once as a TO and once as a FROM node. While this is multiple total cases, this is a clear indication of the node not being an intersection, and instead just a straight street.
* We will determine which of the possible node IDS are intersections.

## Raw Counts
### FROM Nodes
```{r}
# Determine which FROM nodes are intersections
from_node_freq.df <- network.df %>% 
  group_by(from_id) %>% 
  summarise(count = n()) %>%
  ungroup() %>% 
  filter(count > 1) %>%
  arrange(desc(count))

from_node_freq.df
```

### TO Nodes
```{r}
# Determine which FROM nodes are intersections
to_node_freq.df <- network.df %>% 
  group_by(to_id) %>% 
  summarise(count = n()) %>%
  ungroup() %>% 
  filter(count > 1) %>%
  arrange(desc(count))

to_node_freq.df
```

## Consolidate
```{r}
# FROM IDs
from_ids <- from_node_freq.df %>%  pull(from_id) %>% unique()
glue('Number of unique nodes - TO:\t{length(from_ids)}')

# To IDs
to_ids <- to_node_freq.df %>%  pull(to_id) %>% unique()
glue('Number of unique nodes - FROM:\t{length(to_ids)}')

# Combine and reduce to unique
intersection_ids <- unique(c(from_ids, to_ids))

glue('Number of nodes - intersection:\t{length(intersection_ids)}')
glue('Number of nodes - all:\t\t{n_edge_post}')
```

```{r}
network.df %>% 
  filter(edge_id %in% seq(213040, 213050, 1))
```


# Subset Street Network

```{r}
# Define subsetting Parameters
center_lat <- 35.242974
center_lon <- -80.794735
radius <- 1000

# Execute
network_subset.df <- subset_lat_lon(
  network    = network.df, 
  lat_center = center_lat, 
  lon_center = center_lon,
  radius     = radius 
    )

```

# Define Node-to-Node Segments 
```{r}
network <- network_subset.df

# Initialize segment id column
blank_tag <- "<empty>"
network <- network %>% 
  mutate(segment_id = blank_tag)

iter_count <- 0

start_time <- Sys.time()

# Execute function while any
while (any(network$segment_id == blank_tag)) {
  
  iter_count <- iter_count + 1
  # print(glue('Iteration:\t\t{iter_count}'))
  
  # Segment ID
  ## Extract used segment ids
  utilized_segment_ids <- network %>% 
    select(segment_id) %>% 
    drop_na() %>% 
    pull()
  
  ## Generate new segment ID
  segment_id_random <- randomID(utilized_segment_ids)
  # print(glue('Segment ID:\t\t{segment_id_random}'))
    
  # Randomly select edge_id of row with segment_id == NA
  select_edge_id <- network %>% 
    filter(segment_id == blank_tag) %>% 
    sample_n(1) %>% 
    pull(edge_id)
  
  # Initialize recurse counter
  recurse_count <- 0
  
  # Walk through network
  network <- walk_streets(
    network.df        = network, 
    input_edge_id     = select_edge_id, 
    segment_id_random = segment_id_random,
    n_recurse         = recurse_count
   )
 
 if ((iter_count %% 1e3) == 0) {
   print(glue('Number of iterations: {iter_count}'))
 }
 
 if (iter_count > 1e6){
   print(glue('Maximum iterations reached.'))
   break
 }
  
  # print(glue(""))

}

end_time <- Sys.time()
time_elapsed <- round(
  difftime(
    end_time, start_time,
    units = c("secs")
    ),
  1)

nodes <- unique(c(network$from_id, network$to_id))
n_intersections <- length(nodes[nodes %in% intersection_ids])
n_segments <- length(unique(network$segment_id))

glue('Number of iterations:\t\t\t\t{iter_count}')
glue('Number of edges - pre-processing:\t\t{length(network$edge_id)}')
glue('Number of edges - post processing:\t\t{length(network$edge_id)}')
glue('Number of segments:\t\t\t\t{n_segments}')
glue('Number of intersections:\t\t\t{n_intersections}')
glue('Time Elapsed:\t\t\t\t\t{time_elapsed} seconds')
```


# Global Preprocessing
## Check point
```{r}
network_no_processing.df <- network
network_no_processing.df
```

## Calculate Edge Centerpoint
```{r}
network.df <- network_no_processing.df %>% 
  mutate(
    center_lat = (to_lat + from_lat)/2,
    center_lon = (to_lon + from_lon)/2
  )
```

## Calculate Angle of Edge
* Assume x-axis and y-axis are at zero
* Radians are expressed in units of pi
* Angles are relative to the x axis at y = 0

```{r}
# Calculate Angle of road segment
network.df <- network.df %>% 
  mutate(
    theta_pi_rad = atan2(
      y = to_lat - from_lat,
      x = to_lon - from_lon
      ) / pi ,
    theta_pi_rad = if_else(
      theta_pi_rad < 0, 
      theta_pi_rad + 1,
      theta_pi_rad
      )
  )

angles <- network.df %>% pull(theta_pi_rad)
print(glue("Maximum angle: {round(max(angles),3)} pi"))
print(glue("Minimum angle: {min(angles)} pi"))
```

## Calculate Angle of Orthogonal Projection
* Shift everything counter clockwise 90 degrees
```{r}
network.df <- network.df %>% 
  mutate(
    theta_pi_orth = theta_pi_rad + 1/2,
    theta_pi_orth = if_else(
      theta_pi_orth >= 2, 
      theta_pi_orth - 2, 
      theta_pi_orth
      )
  )

angles <- network.df %>% pull(theta_pi_orth)
print(glue("Maximum angle: {round(max(angles),3)} pi"))
print(glue("Minimum angle: {min(angles)} pi"))
```
### Inspect
```{r}
start_edge_id <- 683214
network.df %>% 
  filter(edge_id == start_edge_id)
```

## Calculate Length of Opposite and Adjacent
```{r}
## Adjus by 2PI to account for differences in projection direction
dist_m = 10 * (2 * pi)
m_to_deg = 111000
orth_deg <- dist_m/m_to_deg

network.df <- network.df %>% 
  mutate(
    orth_x = orth_deg * cos(theta_pi_orth*pi),
    orth_y = orth_deg * sin(theta_pi_orth*pi),
    len_check_orth = round(sqrt(orth_y^2 + orth_x^2) - orth_deg, 7) == 0,
    to_lat_orth = (center_lat + orth_y),
    to_lon_orth = (center_lon + orth_x),
    from_lat_orth = (center_lat - orth_y),
    from_lon_orth = (center_lon - orth_x),
  )
```

### Inspect
```{r}
start_edge_id <- 683214
network.df %>% 
  filter(edge_id == start_edge_id)
```

```{r}
network.df %>% 
  filter(edge_id == start_edge_id) %>% 
  ggplot() +
  geom_segment(
    mapping = aes(
      x      = from_lon,
      xend   = to_lon,
      y      = from_lat,
      yend   = to_lat
      ), color = "blue"
    ) + 
  geom_segment(
    mapping = aes(
      x      = from_lon_orth,
      xend   = to_lon_orth,
      y      = from_lat_orth,
      yend   = to_lat_orth
      ), color = "red"
    ) +
    coord_map() +
    theme(legend.position = "none")
```

## Create LINESTRING
```{r}
# Normal
network.sf <- makeLinestringVector(network.df, orthogonal = FALSE)

network.sf %>% head()
```

## Calculate Slope of Edge
* Assume x-axis and y-axis are at zero
```{r}
# Calculate Angle of road segment
network.sf <- network.sf %>% 
  mutate(
    m_edge = (to_lon - from_lon) / (to_lat - from_lat),
    m_orth = (to_lon_orth - from_lon_orth) / (to_lat_orth - from_lat_orth),
    m_check = round(abs(m_edge * m_orth) - 1,5)
  ) 

network.sf
```

## Check Line Length
We need to check that thelat 2D line projection has the correct length, and we can look at how the flat length compares to the projected length.
```{r eval=FALSE}
# 
# network.df <- sf::st_drop_geometry(network.sf)
# 
# inspect_length <- network.df %>% 
#   mutate(
#       length_flat = purrr::pmap_dbl(
#         .l = list(
#           lat_1 = to_lat_orth,
#           lon_1 = to_lon_orth,
#           lat_2 = from_lat_orth,
#           lon_2 = from_lon_orth,
#           proj  = FALSE
#           ), 
#           .f = line_length
#       ),
#       length_proj = purrr::pmap_dbl(
#         .l = list(
#           lat_1 = to_lat_orth,
#           lon_1 = to_lon_orth,
#           lat_2 = from_lat_orth,
#           lon_2 = from_lon_orth,
#           proj  = TRUE
#           ), 
#           .f = line_length
#       ),
#       length_delta = length_flat - length_proj,
#       length_per_diff = round(100* length_delta/length_proj,2),
#       length_ratio = round(length_flat/length_proj,2)
#   ) %>% 
#   select(
#     theta_pi_rad, theta_pi_orth, length_flat, length_proj, length_delta, 
#     length_per_diff, length_ratio
#     )
# 
# inspect_length %>% 
#   mutate(max_ratio = max(length_ratio)) %>% 
#   arrange(desc(length_ratio)) %>% 
#   head(5)
# 
# 
# inspect_length %>% 
#   mutate(max_ratio = max(length_ratio)) %>% 
#   arrange(desc(length_ratio)) %>% 
#   tail(5)

```

Testing for each edge
1. Select edge
2. Filter by radius equal to pi*x + safety factor
3. Filter by edge angle
4. Convert orthogonal projection into linestring
5. Check intersection between orthogonal projection and all remaining linestrings
6. All that intersect add to list of edgeids

# Test Parallel Identification Process
## Checkpoint
```{r}
test.sf <- network.sf
test.sf
```


## Calculate Edge Length
```{r}
test.sf <- test.sf %>% 
  mutate(
      edge_length_flat = purrr::pmap_dbl(
        .l = list(
          lat_1 = to_lat,
          lon_1 = to_lon,
          lat_2 = from_lat,
          lon_2 = from_lon,
          proj  = FALSE
          ), 
          .f = line_length
      )
  )

test.sf
```


```{r}
test.sf %>% 
  dplyr::filter(
    segment_id == "oes2d1nz49"
  )
```


## Select Edge
* Longest Segment

### Method for Selecting Longest Segemnt
```{r}
# Reduce to longest segment
segment_id_iter <- test.sf %>% 
  sf::st_drop_geometry() %>% 
  group_by(segment_id) %>% 
  summarise(length = sum (edge_length_flat)) %>% 
  ungroup() %>% 
  arrange(desc(length)) %>% 
  top_n(n = 1, wt = length) %>% 
  pull(segment_id)

# Reduce to edges
start_edge_ids <- test.sf %>% 
  filter(segment_id == segment_id_iter) %>% 
  pull(edge_id)

# Select Single Edge
start_edge_id <- start_edge_ids[1]
```

### Manual Selection
```{r}
start_edge_id <- 683214
segment_id_iter <- test.sf %>% 
  filter(edge_id == start_edge_id) %>% 
  pull(segment_id)
```

### Extract Parameters
```{r}
# Extract Edge Parameters
start_edge_id.sf <- test.sf %>% 
  filter(edge_id == start_edge_id)

lat_center <- start_edge_id.sf %>% pull(center_lat)
lon_center <- start_edge_id.sf %>% pull(center_lon)
angle <- start_edge_id.sf %>% pull(theta_pi_rad)

lat_orth_to <- start_edge_id.sf %>% pull(to_lat_orth)
lon_orth_to <- start_edge_id.sf %>% pull(to_lon_orth)
lat_orth_from <- start_edge_id.sf %>% pull(from_lat_orth)
lon_orth_from <- start_edge_id.sf %>% pull(from_lon_orth)

angle <- start_edge_id.sf %>% pull(theta_pi_rad)

# Highlight Edge
test.sf <- test.sf %>% mutate(
  highlight = if_else(edge_id == start_edge_id, "test", "other")
)

start_edge_id.sf
```


### Visual Check
```{r}
df <- test.sf

p <- df %>% 
  ggplot() +
  geom_segment(
    mapping = aes(
      x      = from_lon,
      xend   = to_lon,
      y      = from_lat,
      yend   = to_lat,
      color  = highlight,
      text_1 = edge_id,
      text_2 = segment_id,
      text_3 = to_id,
      text_4 = from_id
      )
    ) + 
    coord_map() +
    theme(legend.position = "none")

plotly::ggplotly(p)
```

```{r}

df %>% 
  filter(
    edge_id == 677563
  ) 

df %>% 
  filter(
    segment_id == "oes2d1nz49"
  ) 


inspect_node <- 5514326164

df %>% 
  filter(
    (to_id == inspect_node) | 
    (from_id == inspect_node)
  ) 
```


* For each edge ID: 
* Look for nodes directly orthogonal +- error
* See if that node is an intersection
* if so, split segment

## Subset by Radius
```{r}
# Define Radius
radius_m = 10
safety_buffer = 0.10
radius_adj <- radius_m * 2 * pi * (1 + safety_buffer)


test_subset_radius.sf <- subset_lat_lon(
  network    = test.sf, 
  lat_center = lat_center, 
  lon_center = lon_center,
  radius     = radius_adj 
    )

print(glue('Number of Edges - Total:\t{length(test.sf$edge_id)}'))
print(glue('Number of Edges - Subset:\t{length(test_subset_radius.sf$edge_id)}'))
```

### Visual Check
```{r}
df <- test_subset_radius.sf

p <- df %>% 
  ggplot() +
  geom_segment(
    mapping = aes(
      x      = from_lon,
      xend   = to_lon,
      y      = from_lat,
      yend   = to_lat,
      color  = highlight, 
      text_1 = edge_id,
      text_2 = segment_id,
      )
    ) + 
    coord_map() +
    theme(legend.position = "none")

plotly::ggplotly(p)
```

## Subset by Angle
```{r}
# Define Angle and buffer
angle_inverse <- angle - 2
angle_inverse
angle_buffer <- 0.005
angle_max <- angle + angle_buffer
angle_min <- angle - angle_buffer
angle_inv_max <- angle_inverse + angle_buffer
angle_inv_min <- angle_inverse - angle_buffer

test_subset_radius_angle.sf <- test_subset_radius.sf %>% 
  filter(
    (
      between(
        x     = theta_pi_rad,
        left  = angle_min, 
        right =  angle_max
        ) 
      ) | 
      between(
        x     = theta_pi_rad,
        left  = angle_inv_min, 
        right =  angle_inv_max
      )
      
  )

print(glue('Number of Edges - Total:\t{length(test_subset_radius.sf$edge_id)}'))
print(glue('Number of Edges - Subset:\t{length(test_subset_radius_angle.sf$edge_id)}'))
```

### Visual Check
```{r}
df <- test_subset_radius_angle.sf

p <- df %>% 
  ggplot() +
  geom_segment(
    mapping = aes(
      x      = from_lon,
      xend   = to_lon,
      y      = from_lat,
      yend   = to_lat,
      color  = highlight, 
      )
    ) + 
    coord_map() +
    theme(legend.position = "none")

plotly::ggplotly(p)
```

## Remove Same Segment Pieces
```{r}
test_subset_radius_angle_seg.sf <- test_subset_radius_angle.sf %>% 
  filter(segment_id != segment_id_iter)

test_subset_radius_angle_seg.sf
```

### Visual Check
```{r}
df <- test_subset_radius_angle_seg.sf

p <- df %>% 
  ggplot() +
  geom_segment(
    mapping = aes(
      x      = from_lon,
      xend   = to_lon,
      y      = from_lat,
      yend   = to_lat,
      color  = highlight, 
      )
    ) + 
    coord_map() +
    theme(legend.position = "none")

plotly::ggplotly(p)
```

## Create Orthogonal LINESTRING
```{r}
# Create orthogonal linestring
ls_orth <- start_edge_id.sf %>%
  sf::st_drop_geometry() %>% 
    select(from_lon_orth, from_lat_orth, to_lon_orth, to_lat_orth) %>% 
    rename_with(~gsub("_orth", "", .x)) %>% 
      purrr::pmap(makeLinestring) %>% 
      sf::st_as_sfc(crs = 4326) %>% 
      {
        tibble(
          edge_id = start_edge_id.sf$edge_id, 
          geometry = .)
      } %>% 
  pull(geometry)

# Pull Normal linestring for verification
ls_norm <- start_edge_id.sf %>%
  pull(ls_norm)
start_edge_id.sf

sf::st_intersects(ls_orth, ls_norm, sparse = FALSE)[[1]]
```

```{r}
ggplot() +
  geom_sf(
    data = ls_norm, color = "red"
    ) + 
  geom_sf(
    data = ls_orth, color = "blue"
    ) + 
    coord_sf() +
    theme(legend.position = "none")
```


## Test Intersection
```{r}
ls_set <- test_subset_radius_angle_seg.sf %>% pull(ls_norm)

edge_parallel_iter <- c()
segment_parallel_iter <- c()

test.sf$parallel_segments <- list(c("<EMPTY>"))
test.sf$parallel_edges <- list(c("<EMPTY>"))
test.sf$n_parallel_segments <- as.integer(-1)


for (i in seq_along(test_subset_radius_angle_seg.sf$edge_id)){
  df <- test_subset_radius_angle_seg.sf %>% slice(i)
  
  ls_test <- df %>% pull(ls_norm)
  edge_id_test <- df %>% pull(edge_id)
  segment_id_test <- df %>% pull(segment_id)
  
  bool_intersect <- sf::st_intersects(
    ls_orth, ls_test, sparse = FALSE)[[1]]

  if (bool_intersect) {
    edge_parallel_iter    <- c(edge_parallel_iter, edge_id_test)
    segment_parallel_iter <- c(segment_parallel_iter, segment_id_test)
  }
  
}

test.sf <- test.sf %>% 
  mutate(
    parallel_segments = if_else(
      edge_id == start_edge_id, 
      list(segment_parallel_iter), 
      parallel_segments
    ),
    n_parallel_segments = if_else(
      edge_id == start_edge_id, 
      length(segment_parallel_iter),
      n_parallel_segments
    ),
    parallel_edges = if_else(
      edge_id == start_edge_id, 
      list(edge_parallel_iter),
      parallel_edges
    )
  )

test.sf %>% 
  filter(edge_id == start_edge_id) %>% 
  pull(parallel_segments) %>% 
  unlist()

test.sf
```

# Consolidate Process
## Exit Function
```{r}
exit_parallel_check <- function(
  network, select_edge_id, fail = FALSE, 
  parallel_edges_input = NA, 
  parallel_segments_input = NA
  ) {
  if(fail) {
    
    network %>% 
      mutate(
        n_parallel_segments = dplyr::if_else(
          condition = (edge_id == select_edge_id),
          true      = 0, 
          false     = n_parallel_segments
          )
        )
  } else {
    
    network %>% 
      mutate(
        parallel_segments = dplyr::if_else(
          condition = (edge_id == select_edge_id),
          true      = list(parallel_segments_input),
          false     = parallel_segments
        ),
        n_parallel_segments = dplyr::if_else(
          condition = (edge_id == select_edge_id),
          true      = as.double(length(parallel_segments_input)),
          false     = n_parallel_segments
        ),
        parallel_edges = dplyr::if_else(
          condition = (edge_id == select_edge_id),
          true      = list(parallel_edges_input),
          false     = parallel_edges
        )
      )
  }
}

```



## Pre-process Data
```{r}
network.df <- network_no_processing.df

# Subset
subset_segment_ids <- c("vw0cr0qcv8", "e6pqpcid6a", "ujs01f68lg")

network.df <- network.df %>% 
  filter(segment_id %in% subset_segment_ids)

# PROCESSING ##################################################################

# Calculate edge centerpoint
network.df <- network.df %>% 
  dplyr::mutate(
    center_lat = (to_lat + from_lat)/2,
    center_lon = (to_lon + from_lon)/2
  )

# Calculate edge angle to normal x,y axis. Angle is reported in units of pi 
# radians. Invert all negative angles.
network.df <- network.df %>% 
  dplyr::mutate(
    theta = atan2(
      y = to_lat - from_lat,
      x = to_lon - from_lon
      ) / pi ,
    theta = if_else(
      theta < 0, 
      theta + 1,
      theta
      )
  )

# Calculate angle of orthogonal projection to the edge. This is done by shifting
# the edge angle clockwise by by 1/2.
network.df <- network.df %>% 
  dplyr::mutate(
    theta_orth = theta + 1/2,
    theta_orth = if_else(
      theta_orth >= 2, 
      theta_orth - 2, 
      theta_orth
      )
  )

# Determine points of orthogonal projection. Because our data is representing
# a real world area, a 2D rendering is only a approximation. This affects the 
# implementation of length, which we need to determine the start and end 
# points of the orthogonal projection. Depending on the angle of the orthogonal 
# projection, length in the 2D space could be off by as much as a factor of 
# 2 PI. Therefore, in order for the length calculation to be conservative, we 
# will use a 2 PI factor to adjust the 2D length.

dist_adj_factor <- 2 * pi
dist_m = 15 
dist_adj <- dist_m * dist_adj_factor
m_to_deg = 111000
orth_deg <- dist_m/m_to_deg

network.df <- network.df %>% 
  dplyr::mutate(
    orth_x        = orth_deg * cos(theta_orth*pi),
    orth_y        = orth_deg * sin(theta_orth*pi),
    to_lat_orth   = (center_lat + orth_y),
    to_lon_orth   = (center_lon + orth_x),
    from_lat_orth = (center_lat - orth_y),
    from_lon_orth = (center_lon - orth_x),
  )

# Create Edge LINESTRING
network.sf <- makeLinestringVector(df = network.df, orthogonal = FALSE) %>% 
  select(ls_norm, everything())

# Determine Edge Length
network.sf <- network.sf %>% 
  dplyr::mutate(
    edge_length_m = as.vector(sf::st_length(ls_norm))
  )

# Initialize Parallel Process columns
network.sf <- network.sf %>% 
  dplyr::mutate(
    parallel_edges      = list(c("<EMPTY>")),
    parallel_segments   = list(c("<EMPTY>")),
    n_parallel_segments = -1,
  )

# Create Orthogonal Projection linestrings
network_orth.sf <- makeLinestringVector(
  df = network.df, 
  orthogonal = TRUE
  ) %>% 
  select(edge_id)
```

## Define Constants and Initial Values
```{r}
# Constants
## Radius
radius_m <- 10
safety_buffer <- 0.10
radius_adj <- radius_m * 2 * pi * (1 + safety_buffer)

## Angle
angle_buffer <- 0.005
angle_max <- angle + angle_buffer
angle_min <- angle - angle_buffer

# Initial
while_check.sf <- network.sf %>% filter(n_parallel_segments == -1)
n_remaining <- length(while_check.sf$edge_id)
```


## Execute Loop
```{r}
start_time <- Sys.time()
i <- 1

while (n_remaining > 0){
  
  # Escape Valve
  if(i %% 1e2 == 0) {
    end_time <- Sys.time()

    time_elapsed <- round(
      difftime(
        end_time, start_time,
        units = c("secs")
        ),
      1)
    print(glue(paste0(rep(x = "_", 80), collapse = "")))
    print(glue('Iteration:\t\t\t\t{i}'))
    print(glue('Time Elapsed:\t\t\t\t{time_elapsed} seconds'))
  }
  
  if(i %% 1e5 == 0) {
    break
  }
  
  print(glue(paste0(rep(x = "_", 80), collapse = "")))
  print(glue('Iteration:\t\t\t\t{i}'))
  
  # Select random row
  iter.df <- network.sf %>% 
    filter(n_parallel_segments == -1) %>% 
    dplyr::slice_sample(n = 1)
  
  # Extract Inputs
  edge_id_iter    = iter.df %>% pull(edge_id)
  center_lat      = iter.df %>% pull(center_lat)
  center_lon      = iter.df %>% pull(center_lon)
  segment_id_iter = iter.df %>% pull(segment_id)
  
  print(glue('Edge ID:\t\t\t\t{edge_id_iter}'))
  print(glue('Number of Edges - Total:\t\t{length(network.sf$edge_id)}'))
  
  # Subset Network
  ## Radius
  network_subset.sf <- subset_lat_lon(
    network    = network.sf, 
    lat_center = center_lat, 
    lon_center = center_lon,
    radius     = radius_adj 
      )
  
  n_subset <- length(network_subset.sf$edge_id)
  print(glue('Number of Edges - Subset - Radius:\t{n_subset}'))
  
  if (n_subset == 0) {
    network.sf <- exit_parallel_check(
      network        = network.sf,
      select_edge_id = edge_id_iter, 
      fail           = TRUE
      )
    i <- i + 1
    
    while_check.sf <- network.sf %>% filter(n_parallel_segments == -1)
    n_remaining <- length(while_check.sf$edge_id)
    
    next
  }
  
  ## Subset Angle
  network_subset.sf <- network_subset.sf %>% 
    filter(
      between(
        x     = theta,
        left  = angle_min, 
        right = angle_max
        )
    )
  
  n_subset <- length(network_subset.sf$edge_id)
  print(glue('Number of Edges - Subset - Angle:\t{length(network_subset.sf$edge_id)}'))
  
  if (n_subset == 0) {
    network.sf <- exit_parallel_check(
      network        = network.sf,
      select_edge_id = edge_id_iter, 
      fail           = TRUE
      )
    
    while_check.sf <- network.sf %>% filter(n_parallel_segments == -1)
    n_remaining <- length(while_check.sf$edge_id)
    
    i <- i + 1 
    
    while_check.sf <- network.sf %>% filter(n_parallel_segments == -1)
    n_remaining <- length(while_check.sf$edge_id)
    next
  }
  
  ## Remove edges in the same segment
  network_subset.sf <- network_subset.sf %>% 
    filter(segment_id != segment_id_iter)  
    
  n_subset <- length(network_subset.sf$edge_id)
  print(glue('Number of Edges - Subset - Segment ID:\t{length(network_subset.sf$edge_id)}'))
  
  if (n_subset == 0) {
    network.sf <- exit_parallel_check(
      network        = network.sf,
      select_edge_id = edge_id_iter, 
      fail           = TRUE
      )
    i <- i + 1 
    next
  }
  
  # PARALLEL CHECK ############################################################
  # Initialize
  parallel_edges_iter <- c()
  parallel_segments_iter <- c()
  
  for (comparison_edge_idx in seq_along(network_subset.sf$edge_id)){
    
    # Select orthogonal linestring to check intersection
    ls_orth <- network_orth.sf %>% 
      filter(edge_id == edge_id_iter) %>% 
      pull(ls_orth)
    
    # Select Row to compare
    row_comp <- network_subset.sf %>% slice(comparison_edge_idx)
    
    # Extract parameters for comparison  
    ls_comp         <- row_comp %>% pull(ls_norm)
    edge_id_comp    <- row_comp %>% pull(edge_id)
    segment_id_comp <- row_comp %>% pull(segment_id)
    
    # Check if the orthogonal projection and edge intersect
    ls_intersect <- sf::st_intersects(
      ls_orth, ls_comp, 
      sparse = FALSE
      )[[1]]
    
    # Document edge and segment if they did intersect
    if (ls_intersect) {
      parallel_edges_iter    <- c(parallel_edges_iter, edge_id_comp)
      parallel_segments_iter <- c(parallel_segments_iter, segment_id_comp)
    
    }
    
    print(glue(paste0(rep(x = "-", 80), collapse = "")))
    print(glue("Edge ID:\t\t\t\t{edge_id_iter}"))
    print(glue("Edge ID - Comparison:\t\t\t{edge_id_comp}"))
    print(glue("Segment ID:\t\t\t\t{segment_id_iter}"))
    print(glue("Segment ID - Comparison:\t\t{segment_id_comp}"))
    print(glue("Intersect:\t\t\t\t{ls_intersect}"))
    print(glue(paste0(rep(x = "-", 80), collapse = "")))
    
  }
  
  # Check if any edges were found to be parallel
  if (length(segment_parallel_iter) > 0){
    network.sf <- exit_parallel_check(
      network                 = network.sf, 
      select_edge_id          = edge_id_iter, 
      fail                    = FALSE, 
      parallel_edges_input    = edge_parallel_iter,
      parallel_segments_input = segment_parallel_iter
      
      )
  } else{
    network.sf <- exit_parallel_check(
      network        = network.sf,
      select_edge_id = edge_id_iter, 
      fail           = TRUE
      )
  }
  
  
  while_check.sf <- network.sf %>% filter(n_parallel_segments == -1)
  n_remaining <- length(while_check.sf$edge_id)
  
  i <- i + 1
}

```



## Check Segments with Multiple Edges
```{r}
unique_parallel_segments <- network.sf %>% 
  sf::st_drop_geometry() %>% 
  select(edge_id, segment_id, parallel_segments, parallel_edges) %>% 
  unnest(cols = parallel_segments) %>% 
  unnest(cols = parallel_edges) %>% 
  filter(parallel_segments != "<EMPTY>") 

network.sf

# %>% 
  # group_by(segment_id) %>% 
  # count(parallel_segments)  %>% 
  # ungroup() %>% 
  # group_by(segment_id) %>% 
  # summarise(unique_parallel_segments = n()) %>% 
  # arrange(desc(unique_parallel_segments))

unique_parallel_segments
```

## Known Issue
* long: vw0cr0qcv8
* short 1: e6pqpcid6a
* short 2: usj01f68lg
```{r}

long <- "vw0cr0qcv8"
short_1 <- "e6pqpcid6a"
short_2 <- "ujs01f68lg"

inspect.df <- network.sf %>% 
  sf::st_drop_geometry() %>% 
  filter(segment_id == short_2) %>% 
  unnest(parallel_segments) %>% 
  unnest(parallel_edges) %>% 
  select(edge_id, segment_id, center_lat, center_lon, parallel_edges, parallel_segments)

inspect.df
```

```{r}
inspect_edges <- inspect.df %>% pull(edge_id)

inspect_edges

orth.sf <- network_orth.sf %>% 
  filter(edge_id %in% inspect_edges) 

  ggplot(data = orth.sf) + 
  geom_sf() +
  coord_sf() +
  theme(legend.position = "none")
```


    coord_map() +
    theme(legend.position = "none")# TO DO:
Consolidate to a list of parallel segment ids for each segment id
Check that if any list contains multiple
If multiple, are any of the group connected
If a segment id is parallel to two connected segment ids, then that segment id will be split
Split based on where an orthogonal projection at the shared point would intersect






