---
title: "Exploration"
author: "Evan Canfield"
date: "7/30/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Purpose
Determine how to ensure roads represented as two parallel lines have the same segment intersections on both sides of the line.

# Import
## Packages
```{r import_packages}
if (!require(pacman)) {install.packages("pacman")}
pacman::p_load(
  glue,
  parallel,
  sf,
  stringi,
  tidyverse
)

# Import custom functions
r_files <- list.files("./../R/", full.names = TRUE)
for (file in r_files) {
  source(file)
}

# Set randomized seed
set.seed(5590)
```

## Data
### Street Map
```{r import_data}
# Street network data.frame
# Network has already been assigned segments, and cases where parallel edges 
# need to be split have been identified.

file_dir <- "./../data/"
file_name <- "segmented_street_network_parallel_cases_labeled_10km.RDS"
file_path <- file.path(file_dir, file_name)
network_raw.sf <- readRDS(file_path)
```

### Segment Map
```{r}
segment_map <- read_rds(file = "./../data/segment_mapping_nested.RDS")
```


### Save Copy of Network Dataset
```{r}
network.sf <- network_raw.sf
network.df <- network.sf %>% sf::st_drop_geometry()
```

# Visual
## Process Dataset
```{r}
# Table of all segments with parallel segments, long form
segment_breakdown <- network.df %>% 
  select(edge_id, segment_id, parallel_segments, parallel_edges) %>% 
  unnest(cols = parallel_segments) %>% 
  unnest(cols = parallel_edges) %>% 
  filter(parallel_segments != "<EMPTY>") %>% 
  group_by(segment_id) %>%
  count(parallel_segments) %>% 
  ungroup() %>% 
  rename(
    parallel_segment = parallel_segments,
    n_parallel_edges = n
    ) %>% 
  arrange(segment_id, parallel_segment)

# Summary table of the number of unique parallel segments
unique_parallel_segments <- segment_breakdown %>% 
  group_by(segment_id) %>%
  summarise(unique_parallel_segments = n()) %>%
  arrange(desc(unique_parallel_segments))

# Extract Segments to Highlight
## Long
long_segments <- unique_parallel_segments %>% 
  filter(unique_parallel_segments > 1) %>% 
  pull(segment_id)

## Short
short_segments_1 <- segment_breakdown %>% 
  filter(segment_id %in% long_segments) %>% 
  group_by(segment_id) %>% 
  mutate(row = row_number()) %>% 
  filter(row == 1) %>% 
  pull(parallel_segment)

short_segments_2 <- segment_breakdown %>% 
  filter(segment_id %in% long_segments) %>% 
  group_by(segment_id) %>% 
  mutate(row = row_number()) %>% 
  filter(row == 2) %>% 
  pull(parallel_segment)
```

## Generate Plot
```{r}
# Create column for highlighting the plot
network.df <- network.df %>% 
  mutate(
    highlight = dplyr::case_when(
      segment_id %in% long_segments ~ "long", 
      segment_id %in% short_segments_1 ~ "short_1",
      segment_id %in% short_segments_2 ~ "short_2",
      TRUE ~ "default"
    )
  )

print(glue("Number of Cases: {length(long_segments)}"))

# Generate Plot
p <- plotStreets(network.df, color_feature = "highlight")

# Apply color palette
color_pal <- c(
  "short_1" = "#E71D36", 
  "short_2" = "#FF9F1C",
  "long"    = "#2EC4B6", 
  "default" =  "#D6DBDF"
  )

p <- p + scale_colour_manual(values=color_pal)

# Generate interactive plot
plotly::ggplotly(p)
```

# Define Functions
```{r}
# Verify segments are adjacent
verifyAdjacentSegments <- function(segment_1, segment_2){
  
  segment_1_adj <- segment_map.v[segment_1][[1]]
  
  segment_2 %in% segment_1_adj
  
}






```

# Processing
## Identify Long/Short/Short Sets
Identify all possible cases where of parallel lines where there is one long edge parallel to two short edges.

### Wrap All Parallel Segments into List Column
```{r}
# Reduce to segments with two or more segment matches
parallel_segments.v <- unique_parallel_segments %>% 
  filter(unique_parallel_segments > 1) %>% 
  pull(segment_id)

# Wrap all short segments into a list column vector
parallel_segments.df <- segment_breakdown %>% 
  rename(long_segment = segment_id) %>% 
  select(-n_parallel_edges) %>% 
  filter(long_segment %in% parallel_segments.v) %>% 
  group_by(long_segment) %>% 
  summarise(parallel_segments = list(unique(parallel_segment))) 

# Explode list column vector of parallel segments into dataframe of all 
# possible pairs of the values within the vector
parallel_segments.df <- parallel_segments.df%>% 
  group_by(long_segment) %>% 
  summarise(listPairs(parallel_segments)) %>% 
  rename(
    short_segment_1 = item_1,
    short_segment_2 = item_2,
  )

parallel_segments.df 
```

### Remove Short Segments Which Are Not Adjacent
```{r}
segment_map.v <- deframe(segment_map)

parallel_segments.df <- parallel_segments.df %>% 
  mutate(
    short_is_adjacent = purrr::pmap_lgl(
      .l = list(
        segment_1 = short_segment_1, 
        segment_2 = short_segment_2
      ), 
      .f = verifyAdjacentSegments
      )
  ) %>% 
  filter(short_is_adjacent)
```

## Determine Slice Point on Long Segment
### Define Example Parameters
Parkwood @ Barry
```{r}
# Defined parameters of 
s1 <- '2dx94g7bo2'
s2 <- 'heyaz2jzyv'
l_seg <- 'l0sztiy7lq'
l_edge_id <- '769046'

s3 <- intersect(segment_map.v[s1][[1]], segment_map.v[s2][[1]])
```

### Create Node and Edges Databases
```{r}
# Nodes
to_id.df <- network.df %>% 
  select(segment_id, to_id, to_lon, to_lat) %>% 
  rename(
    node_id = to_id,
    node_lon = to_lon, 
    node_lat = to_lat
    )

from_id.df <- network.df %>% 
  select(segment_id, from_id, from_lon, from_lat) %>% 
  rename(
    node_id  = from_id,
    node_lon = from_lon, 
    node_lat = from_lat
    )

nodes.df <- bind_rows(to_id.df, from_id.df) %>% 
  distinct()

# Edges
edges.df <- network.df %>% 
  select(edge_id, segment_id, from_id:to_lat)

edges.df
```

### Determine Latitude/Longitude at Short Segment Connection
#### Scratch
```{r}
network_seg_1.df <- nodes.df %>% 
  filter(
    (segment_id == s1) 
)

network_seg_2.df <- nodes.df %>% 
  filter(
    (segment_id == s2) 
  )

seg_1_nodes <- network_seg_1.df %>% pull(node_id)
seg_2_nodes <- network_seg_2.df %>% pull(node_id)

node_intersect <- intersect(seg_1_nodes, seg_2_nodes)

lat_intersect <- nodes.df %>% 
  filter(node_id == node_intersect) %>% 
  pull(node_lat) %>% 
  unique()


lon_intersect <- nodes.df %>% 
  filter(node_id == node_intersect) %>% 
  pull(node_lon) %>% 
  unique()

```


```{r}
x <- list(nodes.df)

x[[1]]
```


```{r}
sharedShortSegmentPoint <- function(segment_id_1, segment_id_2, node_table) {

    # Extract nodes related to segment 1
  seg_1_nodes <- dataframe %>% 
    filter(
      (segment_id == segment_id_1)
    ) %>% 
    pull(node_id)
  
  # Extract nodes related to segment 1
  seg_2_nodes <- dataframe %>% 
    filter(
      (segment_id == segment_id_2)
    ) %>% 
    pull(node_id)
  
  # Determine intersection
  intersect_node <- intersect(seg_1_nodes, seg_2_nodes)
  
  # Determine longitude/latitude of intersection point
  short_intersect_lon <- dataframe %>% 
    filter(node_id == intersect_node) %>% 
    pull(node_lon) %>% 
    unique()
  
  short_intersect_lat <- dataframe %>% 
    filter(node_id == intersect_node) %>% 
    pull(node_lat) %>% 
    unique()
  
  # Export lon/lat vector
  short_intersect_point <- c(short_intersect_lon, short_intersect_lat)
  names(short_intersect_point) <- c('short_intersect_lon', 'short_intersect_lat')
  short_intersect_point
}
```

#### Execute Function
```{r}

parallel_segments.df <- parallel_segments.df %>% 
  mutate(
    short_intersect = 
         purrr::pmap(
           .l = list(
             segment_id_1 = short_segment_1,
             segment_id_2 = short_segment_2,
             node_table   = list(nodes.df)
           ), 
           .f =  sharedShortSegmentPoint
         )
    ) %>%
  unnest_wider(short_intersect)

parallel_segments.df

parallel_segments_raw.df <- parallel_segments.df
```


## Determine Closest Edge and Point in Long Segment to the Intersection Point
##### Inspect
```{r}
x1 <- 1
y1 <- -1.738943
x2 <- 3
y2 <- 30


x.v <- c(x1, x2)
y.v <- c(y1, y2)
cbind(x.v, y.v)

dist(cbind(x.v, y.v))[1]

distPointToPoint(x1,y1, x2, y2)
```

#### Line Slope and Intercept
```{r}
lineSlope <- function(x_1, y_1, x_2, y_2) {
  (y_2 - y_1) / (x_2 - x_1)
}

yIntercept <- function(x, y, slope){
  # y = mx + b >>> b = y - mx
  y - slope * x
}
```


### Generate Segment Edges w/ Line Parameters
```{r}
edges_l_seg.df <- edges.df %>% 
  filter(
    segment_id == l_seg
  ) %>% 
  mutate(

  )

edges_l_seg.df
```


### Determine Shortest Distance From Edge to Point
#### Scratch
```{r}
# # Determine length of edge
# l_edge <- distPointToPoint(edge_from_lon, edge_from_lat, edge_to_lon, edge_to_lat)
# 
# # Generate sequence of x values
# x_seq <- seq(from = edge_from_lon, to = edge_to_lon , by = l_edge/100)
# 
# # Determine corresponding y values along the edge
# y_seq <- m * x_seq + b

```

```{r}
# o = optimize(
#   f = distLineToPoint, x_seq, lon_intersect, lat_intersect, m , b
#   )
# 
# x_min <- o$minimum
# y_min <- m * x_min + b
# 
# y_min - m*x_min - b
```

#### Functionize
```{r}
intersect_lon <- parallel_segments.df %>% 
  filter(long_segment == l_seg) %>% 
  slice(1) %>% 
  pull(short_intersect_lon)

intersect_lat <- parallel_segments.df %>% 
  filter(long_segment == l_seg) %>% 
  slice(1) %>% 
  pull(short_intersect_lat)

```

##### Execute
```{r}
#### Execute Function
edges_l_seg_obj.df <- edges_l_seg.df %>% 
  mutate(
    minimize_distance = 
      purrr::pmap(
        .l = list(
          from_lon      = from_lon,
          to_lon        = to_lon,
          slope         = slope, 
          intercept     = intercept, 
          edge_length   = edge_length,
          lon_intersect = intersect_lon, 
          lat_intersect = intersect_lat,
          x_points      = 1e3
           ), 
        .f =  minimumDistance
         )
    ) %>% 
  unnest_wider(minimize_distance)

edges_l_seg_obj.df %>% 
  filter(objective == min(objective))
```

### Combine To Select Edge
```{r}
parallel_segments_raw.df
longSegmentSplitPoint <- function(
  long_segment, 
  short_intersect_lon, 
  short_intersect_lon, 
  x_points = 1e3
  ){
   # Extract longitude and latitude at short segment connection point
  
  
  # Create table of edges associated with the long segment
  edges_l_seg.df <- edges.df %>% 
  filter(
    segment_id == long_segment
  ) %>% 
  mutate(
    slope       = lineSlope(from_lon, from_lat, to_lon, to_lat), 
    intercept   = yIntercept(from_lon, from_lat, slope),
    edge_length = distPointToPoint(from_lon, from_lat, to_lon, to_lat)
  )
  
  edges_l_seg_obj.df <- edges_l_seg.df %>% 
  `  mutate(
      minimize_distance = 
        purrr::pmap(
          .l = list(
            from_lon      = from_lon,
            to_lon        = to_lon,
            slope         = slope, 
            intercept     = intercept, 
            edge_length   = edge_length,
            lon_intersect = short_intersect_lon, 
            lat_intersect = short_intersect_lon,
            x_points      = x_points
             ), 
          .f =  minimumDistance
           )
      ) %>% 
    unnest_wider(minimize_distance)
  `
  edges_l_seg_obj_min.df <- edges_l_seg_obj.df %>% 
    mutate(
      min_lat = slope * minimum + intercept
    )
    filter(objective == min(objective))
  
  # Extract output values
  split_edge <- edges_l_seg_obj_min.df %>% pull(edge_id)
  split_lon <- edges_l_seg_obj_min.df %>% pull(minimum)
  split_lat <- edges_l_seg_obj_min.df %>% pull(min_lat)
  
  # Create output list
  output_list <- vector(mode = 'list', length = 3)
  output_list[['split_lon']] <- split_lon
  output_list[['split_lat']] <- split_lat
  
  output_list
  
}
```


