---
title: "Exploration"
author: "Evan Canfield"
date: "3/15/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Purpose
Exploration of data visualization.

# Import
## Packages
```{r import_packages}
if (!require(pacman)) {install.packages("pacman")}
pacman::p_load(
  data.table,
  leaflet,
  OpenStreetMap,
  osmdata,
  plotly,
  sf,
  tidyverse
)
```

## Data
### Street Map w/ Tracking
```{r import_data}
# Street network data.frame
clt_network.df <- readRDS("./../data/dodgr_network_charlotte_nc_2021-03-17.RDS")

# Define column type to avoid messages
col_type <- c(
  "edge_id" = "character",
  "to_id" = "character",
  "from_id" = "character",
  "status" = "character"
)

# Status tracking data.frame
tracking.df <- fread(
  file = "./../data/tracking_charlotte_nc_active_2021-03-17.CSV", 
  stringsAsFactors = FALSE,
  colClasses = col_type
  ) 
```

```{r}
clt_network.df
```

```{r}
tracking.df
```

### OpenStreetsMap Background

```{r}
clt_bb <- getbb("Charlotte North Carolina")

clt_bb
clt_bb[1]
clt_bb[2]
clt_bb[3]
clt_bb[4]
```



```{r}

# Download Map
clt_map <- openmap(
  upperLeft = c(clt_bb[2], clt_bb[1]), 
  lowerRight = c(clt_bb[4], clt_bb[3]),
  zoom = NULL,
  type = c("osm"),
  mergeTiles = TRUE
  )

# Convert
clt_map <- openproj(clt_map)

# Plot
OpenStreetMap::autoplot.OpenStreetMap(clt_map)
```


# Processing
We need to join our street network with the tracking status table.
```{r}
# Reduce to essential columns
tracking.df <- tracking.df %>% 
  select(edge_id, status)

# Join status with street network
clt_network.df <- clt_network.df %>% 
  left_join(
    tracking.df,
    by = "edge_id"
    )
```

To verify our join is working correctly we'll check to make sure there are no missing status values post-join.
```{r}
Hmisc::describe(clt_network.df$status)
```

# EDA
```{r}
Hmisc::describe(clt_network.df$highway)
```

```{r}
Hmisc::describe(clt_network.df$to_zip)

clt_network.df %>% 
  group_by(to_zip) %>% 
  summarise(
    freq = round( 100 * n() / nrow(clt_network.df), 2)
    ) %>%
  mutate(
    to_zip = as.numeric(to_zip)
  ) %>% 
  arrange(to_zip)
```

# Data Processing
We'll start out with a simple plot of the 28205 ZIP code. We pick this area due to it's relatively small geographic size and I am familiar with its street layout.
```{r}

select_zip_codes <- c("28201", "28202", "28203", "28204", "28205")

clt_network_demo.df <- clt_network.df %>% 
  filter(
    from_zip %in% select_zip_codes | 
      to_zip %in% select_zip_codes,
    highway != "path"
    )

clt_network_demo.df %>% glimpse()
```

We also need to create a **sf** object for the leaflet visual. We can use **sf** in ggplot as well, so it is easier to just convert the data before all visualization. We'll use the **pmap** function from **purrr** to apply a function which will convert the line segments into LINESTRING objects. Once the geometry is created, we will then join the LINESTRING back to the dataset, and then convert to an **Sf_object**.

```{r}
# Make LINESTRING and convert df to sf object
clt_network_demo.sf <- clt_network_demo.df %>% 
  select(from_lon, from_lat, to_lon, to_lat) %>% 
  pmap(makeLinestring) %>% 
  st_as_sfc(crs = 4326) %>% 
  {tibble(
    edge_id = clt_network_demo.df$edge_id, 
    geometry = .)
    }%>% 
  left_join(
    y = clt_network_demo.df,
    by = "edge_id"
  ) %>% 
  st_sf()


clt_network_demo.sf %>% glimpse()
```

# Visualization
## Static
We'll start out with a simple plot of the 28205 ZIP code. We pick this area due to it's relatively small geographic size and I am familiar with its street layout.

### Color Only
```{r}

df <- clt_network_demo.df

# Subset
street_name = 'Club'
df <- df %>% 
  # filter(tiger.name_base == street_name) %>% 
  filter(edge_id %in% c(213073, 213074, 213075, 213076))

p <- ggplot(data = df) +
  geom_segment(
    mapping = aes(
      x = from_lon,
      xend = to_lon,
      y = from_lat,
      yend = to_lat,
      color = edge_id, 
      text_1 = highway, 
      text_2 = tiger.name_base,
      text_3 = edge_id,
      text_4 = from_id,
      text_5 = to_id
      )
  ) + coord_map()

p
```

```{r}
df
```


### Plotly Conversion

```{r}
ggplotly(p, tooltip = c("color","text_1", "text_2", "text_3",
                      "text_4", "text_5"))
```


## Iteractive

```{r}
m <- leaflet(data = clt_network_demo.sf) %>% 
  addTiles() %>% 
  addPolylines(
    color = status
    ) %>% 
  setView(-80.7912262, 35.245896, zoom = 17)

m
```

