---
title: "Exploration"
author: "Evan Canfield"
date: "7/30/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Purpose
Determine how to use GPS tracking data files to determine where has been walked.

This notebook will walk through the processing of a single GPS event, but will be set expect to iterate over multiple events

# Import
## Packages
```{r import_packages}
if (!require(pacman)) {install.packages("pacman")}
pacman::p_load(
  glue,
  sf,
  tidyverse
)
```

## Data
### Street Map
```{r import_data}
# Street network data.frame
network.df <- readRDS("./../data/dodgr_network_charlotte_nc_2021-03-17.RDS")

# Define column type to avoid messages
col_type <- c(
  "edge_id" = "character",
  "to_id" = "character",
  "from_id" = "character",
  "status" = "character"
)
```

### GPS Tracking Files
```{r}
# Define file directory
file_dir <- "./../data/gps_tracking_files/test_case"

# List all possible files
available_files <- list.files(file_dir)
print(available_files)

# Select file
file_name <- available_files[2]

# Define file path
file_path <- file.path(file_dir, file_name)
print(file_path)

# Show all possible file layers
print(sf::st_layers(file_path))

# Load required layers
tracks.sf <- sf::st_read(dsn = file_path, layer = "tracks")
track_points.sf <- sf::st_read(dsn = file_path, layer = "track_points")
```

# Processing
## Extract Activity Metadata
### Property 1: Activity Occurred with Kelsey
```{r}
# Extract note
activity_note <- tolower(tracks.sf$desc)

# Test if property requirement is met
## Property 1: Activity occurred with Kelsey
property_1_test <- grepl(
  pattern = 'kelsey', 
  activity_note, 
  fixed=TRUE
  )

# Output property 1 condition
property_1_text <- "Property 1 (Activity Occurred With Kelesy): "
glue("{property_1_text} {property_1_test}")
```

### Starting Time of Event
```{r}
activity_timestamp_start <- track_points.sf$time[1]
print(timestamp_start)
```

### Activity Type
```{r}
activity_type <- tracks.sf$type
```

## Initialize Tracking Columns in Street Network
```{r}
network.df <- network.df %>% 
  mutate(
    activity = NA,
    timestamp_start = NA,
    property_1 = FALSE
  )
```


## Reduce Street Network Size
* Start out with subset of the street network
* Use zip code 28205 due to it's relatively small geographic size and personal familiarity with the area
```{r}
# Select zip codes to subset data with
select_zip_codes <- c("28205")

# Subset to selected zip codes
network_demo.df <- network.df %>% 
  filter(
    from_zip %in% select_zip_codes | 
      to_zip %in% select_zip_codes,
    highway != "path"
    )

# network_demo.df %>% glimpse()
```

## Create SF LINSTRING object from Street Segment Latitude/Longitude
* We will us SF object for each street and each gps object. 
* Utilizing SF objects will all us to use SF specific functions to see if a GSP track overlaps with an existing street object.
* We convert the tabular latitude/longitude data into a new column for a LINESTRING object.
```{r}
# LINESTRING Function
make_linestring <- function (from_lon, from_lat, to_lon, to_lat) {
  st_linestring(
    matrix(
      data = c(from_lon, to_lon, from_lat, to_lat), 
      nrow = 2, 
      ncol =  2
      )
    )
}

# Make LINESTRING and convert df to sf object
network_demo.sf <- network_demo.df %>% 
  select(from_lon, from_lat, to_lon, to_lat) %>% 
  pmap(make_linestring) %>% 
  st_as_sfc(crs = 4326) %>% 
  {tibble(
    edge_id = network_demo.df$edge_id, 
    geometry = .)
    }%>% 
  left_join(
    y = network_demo.df,
    by = "edge_id"
  ) %>% 
  st_sf()

network_demo.sf %>% glimpse()
```

# GPS/Street Overlap
## Define Bounding Box of GPS
```{r}
# Extract bounding box
bbox_activity <- sf::st_bbox(tracks.sf$geometry)
bbox_activity
```

## Filter Street Network by Bounding Box
Filter street network dataframe by using the bounding box of the GPS track to limit the street network to only streets within the box.
```{r}
n_streets <- length(network_demo.sf$edge_id)

# Crop network to only streets within the activity bounding box 
# Unsure if this includes streets which are partially in the bounding box
# I expect they are not included. 
network_bbox.sf <- st_crop(
  x = network_demo.sf, 
  y = bbox_activity
  )

# Determine number in subset - total
n_bbox_streets <- length(network_bbox.sf$edge_id)

# Remove streets that have already been assigned an activity
# Not an issue for first activity
network_bbox.sf <- network_bbox.sf %>% filter(is.na(activity))

# Determine number in subset - available
n_bbox_streets_avail <- length(network_bbox.sf$edge_id)

# Generate street count totals, pre and post
n_streets <- length(network_demo.sf$edge_id)
n_bbox_streets <- length(network_bbox.sf$edge_id)

data_reduction <- round(1 - (n_streets - n_bbox_streets_avail) / n_streets, 3 )
data_reduction <- data_reduction

# Print statements to show effect of subset
print(" ")
glue("Streets in Network - Total: {n_streets}")
glue("Streets in Network - Subset - All: {n_bbox_streets}")
glue("Streets in Network - Subset - Available: {n_bbox_streets_avail}")
glue("Effective street network reduced to {data_reduction*100}% of total.")
```

## Check if Activity is in Within Distance of Street Network
### Function
```{r}
within_test <- function(street_linestring, activity_geometry, distance_thresh = 1e-5) {
  
  # Check if LINESTRING is within distance of activity gps track
  st_within_test <- sf::st_is_within_distance(
    x = street_linestring, 
    y = activity_geometry, 
    dist = distance_thresh
  )
  
  # Convert response to binary (Within threshold = 1)
  if (length(st_within_test[[1]]) != 0) {
    response = 1
  } else {
    response = 0
  }
  
  # Export results
  response
}
```


### Test Function
#### Loop
* Execute function in a loop, one observation at a time.
```{r}
# Define distance threshold 
distance_thresh <- 1e-4

# Initialize
sf_within_count <- 0

# Execute loop across bounding box subsetted data
for (geom in network_bbox.sf$geometry){
  
  response <- within_test(
    street_linestring = geom, 
    activity_geometry = tracks.sf$geometry, 
    distance_thresh   = distance_thresh
  )
  
  sf_within_count <- sf_within_count + response
}

# Print statements to show effect of function
n_streets <- length(network_bbox.sf$edge_id)
glue("Total streets in subset: {n_streets}")
glue("Total streets identified within distance threshold: {sf_within_count}")
```

#### Vectorize
* Execute vectorized form of function.
```{r}
# Vectorize function
within_test_v <- Vectorize(within_test, SIMPLIFY = FALSE)

# Modify column with new function
network_bbox.sf <- network_bbox.sf %>% 
  mutate(
    covered = within_test_v(
        street_linestring = geometry,
        activity_geometry = tracks.sf$geometry,
        distance_thresh   = distance_thresh
      )
  ) %>% 
  tidyr::unnest(covered)

# Print statements to show effect of function
street_segments_covered <- sum(network_bbox.sf$covered)
glue("Total streets in subset: {n_streets}")
glue("Total streets identified within distance threshold: {street_segments_covered}")
```

## Apply Metadata
```{r}
# Assign activity metadata for streets identified
network_bbox.sf <- network_bbox.sf %>% 
  mutate(
        activity        = case_when(covered == 1 ~ activity_type),
        timestamp_start = case_when(covered == 1 ~ activity_timestamp_start),
        property_1      = case_when(covered == 1 ~ property_1_test)
  ) %>% 
  select(-covered)
```

```{r}
network_bbox.sf %>% glimpse()
```


## Rejoin with Complete Street Network
```{r}
# Reduce data to only edge ids where an activity was identified
network_activity_id.sf <- network_bbox.sf %>% 
  filter(!is.na(activity)) 

# Extract edge ids
egde_ids_activity <- network_activity_id.sf %>% pull(edge_id)

# Remove edges where the activity was identified
network_demo.sf <- network_demo.sf %>% 
  filter(!(edge_id %in% egde_ids_activity))

# Rebind edges where activities were identified, now with metadata
network_demo_post.sf <- network_demo.sf %>% 
  bind_rows(network_activity_id.sf)
```


# Visualization
## Color Only
```{r}
p <- ggplot(data = network_demo_post.sf) +
  geom_segment(
    mapping = aes(
      x = from_lon,
      xend = to_lon,
      y = from_lat,
      yend = to_lat,
      color = activity, 
      text_1 = highway, 
      text_2 = tiger.name_base,
      text_3 = edge_id,
      text_4 = from_id,
      text_5 = to_id,
      text_6 = geom_num
      )
  ) + coord_map()

p
```


## Plotly Conversion

```{r}
ggplotly(p, tooltip = c("color","text_1", "text_2", "text_3",
                      "text_4", "text_5", "text_6"))
```