---
title: "Exploration"
author: "Evan Canfield"
date: "7/30/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Purpose
Determine how to convert every set of lines that exist between nodes into MULTISTRINGLINES, and then break these lines into equal sized smaller lines.

# Import
## Packages
```{r import_packages}
if (!require(pacman)) {install.packages("pacman")}
pacman::p_load(
  glue,
  sf,
  stringi,
  tidyverse
)

# Import custom functions
r_files <- list.files("./../R/", full.names = TRUE)
for (file in r_files) {
  source(file)
}

# Set randomized seed
set.seed(5590)
```

## Data
### Street Map
```{r import_data}
# Street network data.frame
network_raw.df <- readRDS("./../data/dodgr_network_charlotte_nc_2021-03-17.RDS")

# Define column type to avoid messages
col_type <- c(
  "edge_id" = "character",
  "to_id" = "character",
  "from_id" = "character",
  "status" = "character"
)
```

# Processing
## Drop Duplicates
* There are duplicate rows, with from and to ids swapped
```{r}
# Record number of observations before dropping
n_edge_raw <- length(network_raw.df$edge_id)

# Drop duplicate observations
network.df <- network_raw.df %>% 
    mutate(
    dup_id = if_else(
      from_id > to_id, 
      paste(to_id, from_id, sep = "_"),
      paste(from_id, to_id,  sep = "_")
    )
  )  %>% 
  group_by(dup_id) %>% 
  filter(row_number()==1) %>% 
  ungroup() %>% 
  select(-dup_id)

# Record number of observations after dropping
n_edge_post <- length(network.df$edge_id)

glue('Number of observations - original:\t\t\t{n_edge_raw}')
glue('Number of observations - post duplicate removal:\t{n_edge_post}')
```
### Spot Check
```{r}
network.df %>% 
  filter(
    edge_id %in% seq(213042, 213052, 1)
  )
```

### Highway Types
```{r}
network.df %>% 
  count(highway) %>% 
  arrange(desc(n))
```


### Remove Street Types
```{r}
street_types <- c('path', 'primary_link', 'secondary_link', 'tertiary_link', 'trunk_link', 
                  'living_street')
network.df <- network.df %>% 
  filter(!(highway %in% street_types))
```


# Determine Intersections
* Each **edge_id** is defined by two nodes, and TO and FROM node. 
* If a node is used by multiple edge_ids as a TO or FROM node then we know this node is an intersection.
* A case to be careful of is when a node is used only twice, once as a TO and once as a FROM node. While this is multiple total cases, this is a clear indication of the node not being an intersection, and instead just a straight street.
* We will determine which of the possible node IDS are intersections.

## Raw Counts
### FROM Nodes
```{r}
# Determine which FROM nodes are intersections
from_node_freq.df <- network.df %>% 
  group_by(from_id) %>% 
  summarise(count = n()) %>%
  ungroup() %>% 
  filter(count > 1) %>%
  arrange(desc(count))

from_node_freq.df
```

### TO Nodes
```{r}
# Determine which FROM nodes are intersections
to_node_freq.df <- network.df %>% 
  group_by(to_id) %>% 
  summarise(count = n()) %>%
  ungroup() %>% 
  filter(count > 1) %>%
  arrange(desc(count))

to_node_freq.df
```

## Consolidate
```{r}
# FROM IDs
from_ids <- from_node_freq.df %>%  pull(from_id) %>% unique()
glue('Number of unique nodes - TO:\t{length(from_ids)}')

# To IDs
to_ids <- to_node_freq.df %>%  pull(to_id) %>% unique()
glue('Number of unique nodes - FROM:\t{length(to_ids)}')

# Combine and reduce to unique
intersection_ids <- unique(c(from_ids, to_ids))

glue('Number of nodes - intersection:\t{length(intersection_ids)}')
glue('Number of nodes - all:\t\t{n_edge_post}')
```

```{r}
network.df %>% 
  filter(edge_id %in% seq(213040, 213050, 1))
```


# Subset Street Network
**Zip Code Level**
* Start out with subset of the street network
* Use zip code 28205 due to it's relatively small geographic size and personal familiarity with the area

**Street Level**
* Optional action for testing
* Subset to a single road and all connecting roads
```{r}
# Define possible methods
subset_method <- c('zip', 'street', 'lat_lon', 'highway_type')

# Select method
method <- subset_method[1]
glue('Subset Method: {method}')

if (method == subset_method[1]) {

  # Select zip codes to subset data with
  subset_zip_codes <- c("28205")
  
  glue('Zip code(s) selected : {subset_zip_codes}')
  
  # Subset to selected zip codes
  network_subset.df <- network.df %>% 
    filter(
      (from_zip %in% subset_zip_codes) | 
      (to_zip %in% subset_zip_codes) &
      (highway != "path")
      )
  
  } else if (method == subset_method[2]) {
    # Select street name
    subset_street_names <- c('Dinglewood')
    
    print(glue('Street name(s) selected: {subset_street_names}'))
    
    # Subset network to selected street
    network_subset_name.df <- network.df %>%
      filter(tiger.name_base %in% subset_street_names)
    
    # Extract all nodes
    subset_nodes <- unique(
      c(network_subset_name.df$from_id, 
        network_subset_name.df$to_id)
      )
    
    # Subset network by nods
    network_subset.df <- network.df %>%
      filter(
        (from_id %in% subset_nodes) |
        (to_id %in% subset_nodes) &
        (highway != "path")
      )
  }  else if (method == subset_method[3]) {

    center_lat <- 35.25035
    center_lon <- -80.78195
    radius <- 1e-2
    
    print(glue('Center Latitude: {center_lat}'))
    print(glue('Center Longitude: {center_lon}'))
    print(glue('Radius: {radius}'))
    
    
    network_subset.df <- network.df %>% 
      filter(
        (
          between(
            from_lat,
            (center_lat - radius),
            (center_lat + radius)
          ) &
          between(
            from_lon,
            (center_lon - radius),
            (center_lon + radius)
          )
        )
      )
  } else if (method == subset_method[4]) {

    street_types <- c('trunk', 'living_street', 'unclassified')
    
    network_subset.df <- network.df %>% 
      filter(
        highway %in% street_types
      )
  }

n_edges <- length(network_subset.df$edge_id)
glue('Number of edges: {n_edges}')
```

# Algorithm
## Step By Step Scratch Work
### Initialize Dataframe for this step
```{r}
step_by_step.df <- network_subset.df
```

### Initialize Segment ID Column
```{r}
# step_by_step.df <- step_by_step.df %>% 
#   mutate(segment_id = NA)
# 
# step_by_step.df
```

### Generate Segment ID
```{r}
# # Extract Segment Ids
# utilized_segment_ids <- step_by_step.df %>% pull(segment_id)
# 
# # Drop NA
# utilized_segment_ids <- utilized_segment_ids[!is.na(utilized_segment_ids)]
# 
# # Generate segment IDs
# segment_id_gen <- randomID(utilized_segment_ids)
# 
# segment_id_gen
```

### Randomly Select Row with Segment ID == NA
```{r}
# iter_row_1.df <- step_by_step.df %>% 
#   filter(is.na(segment_id)) %>% 
#   sample_n(1)
# 
# iter_row_1.df
```

### Check if Row is Dead End
```{r}
# TO_node <- iter_row_1.df  %>% pull(to_id)
# bool_dead_end <- !(TO_node %in% step_by_step.df$from_id)
# bool_dead_end
```

### Check if Row TO Node is Intersection
```{r}
# TO_node <- iter_row_1.df  %>% pull(to_id)
# bool_intersection <- TO_node %in% intersection_ids
# 
# bool_intersection
```

### IF Dead End or Intersection, assign sement ID
```{r}
# if (any(bool_dead_end, bool_intersection)){
#   print('if')
#   edge_id_iter <- iter_row_1.df  %>% pull(edge_id)
#   print(edge_id_iter)
#   
#   step_by_step.df <- step_by_step.df %>% 
#     mutate(
#       segment_id = case_when(
#         edge_id == edge_id_iter ~ segment_id_gen,
#         )
#     )
# }

```

### Select Row where TO Node is FROM Node
```{r}
# iter_row_2.df <- step_by_step.df %>% 
#   filter(from_id == TO_node)
# 
# iter_row_2.df
```


## Pre-Process Visualization
```{r}

pre_process.sf <- makeLinestringVector(network_subset.df)

color_feature <- 'highway'
p <- plotStreets(pre_process.sf, color_feature)
plotly::ggplotly(p)
```

## Function
```{r}
# Walk through streets
walk_streets <- function(network.df, input_edge_id, segment_id_random, n_recurse) {
  
  recurse_count <- n_recurse + 1
  
  # Recursion Pit Check
  if (recurse_count > 100) {
    print(glue('Recurse limit reached.'))
    print(glue('Edge ID at Limit: {input_edge_id}'))
    exit()
  }
  
  # print(glue(' Edge: {input_edge_id}'))
  # print(glue('Number of Edge Id(s): {length(input_edge_id)}'))
  
  # ACTION --------------------------------------------------------------------
  # Filter network data to selected edge
  row.df <- network.df %>% 
    filter(
      edge_id == input_edge_id
      ) 
  
  # print(glue('Size of row dataframe: {length(row.df$edge_id)}'))
  
  # Segment ID - Before Processing
  segment_id_exist <- row.df %>% pull(segment_id)
  
  # Assign segment id to selected row
  row.df <- row.df %>% 
    mutate(segment_id = segment_id_random)
  
  # Select TO node
  to_node <- row.df %>% pull(to_id)
  # print(glue('To node: {to_node}'))
  
  # Replace sampled row in main dataset
  network.df <- replaceDataframeRow(network.df, row.df)
  
  # RECURSION CHECKS ----------------------------------------------------------

  # Does Street Continue
  # Determine if the to_node of the current edge continues as the 
  # from node of a different edge
  bool_dead_end <- !(to_node %in% network.df$from_id)
  # print(glue('Dead End:\t\t{bool_dead_end}'))
  
  # Intersection Check
  # Determine if the TO node is an intersection
  bool_intersection <- to_node %in% intersection_ids
  # print(glue('Intersection:\t\t{bool_intersection}'))
  
  # Loop Check
  # This check verifies that the segment we are walking is not a connected 
  # loop, like a track. If we detect it is a loop, we need to break this 
  # process once the loop is complete. 
  bool_loop <- segment_id_exist == segment_id_random
  # print(glue('Loop:\t\t{bool_loop}'))
  # print(glue('Segment - Previous:\t\t{segment_id_exist}'))
  # print(glue('Segment - Current:\t\t{segment_id_random}'))

  if (any(bool_dead_end, bool_intersection, bool_loop)) {
    # print(glue('Return dataframe.'))
    # Return update dataframe
    network.df
    
  } else {
    # print('Continue Walk.')
    # Extract edge_id of subsequent street
    input_edge_id <- network.df %>% 
      filter(from_id == to_node) %>% 
      pull(edge_id)
  
    # Walk
    walk_streets(network.df, input_edge_id, segment_id_random, recurse_count)
  }
}

```


## Execute 
```{r}
# Initialize segment id column
blank_tag <- "<empty>"
network_subset.df <- network_subset.df %>% 
  mutate(segment_id = blank_tag)

df <- network_subset.df

iter_count <- 0

start_time <- Sys.time()

# Execute function while any
while (any(df$segment_id == blank_tag)) {
  
  iter_count <- iter_count + 1
  # print(glue('Iteration:\t\t{iter_count}'))
  
  # Segment ID
  ## Extract used segment ids
  utilized_segment_ids <- df %>% 
    select(segment_id) %>% 
    drop_na() %>% 
    pull()
  
  ## Generate new segment ID
  segment_id_random <- randomID(utilized_segment_ids)
  # print(glue('Segment ID:\t\t{segment_id_random}'))
    
  # Randomly select edge_id of row with segment_id == NA
  select_edge_id <- df %>% 
    filter(segment_id == blank_tag) %>% 
    sample_n(1) %>% 
    pull(edge_id)
  
  # Initialize recurse counter
  recurse_count <- 0
  
  # Walk through network
  df <- walk_streets(
    network.df = df, 
    input_edge_id = select_edge_id, 
    segment_id_random = segment_id_random,
    n_recurse = recurse_count
   )
 
 if ((iter_count %% 1e3) == 0) {
   print(glue('Number of iterations: {iter_count}'))
 }
 
 if (iter_count > 1e6){
   print(glue('Maximum iterations reached.'))
   break
 }
  
  # print(glue(""))

}

end_time <- Sys.time()
time_elapsed <- round(
  difftime(
    end_time, start_time,
    units = c("secs")
    ),
  1)

nodes <- unique(c(df$from_id, df$to_id))
n_intersections <- length(nodes[nodes %in% intersection_ids])
n_segments <- length(unique(df$segment_id))

glue('Number of iterations:\t\t\t\t{iter_count}')
glue('Number of edges - pre-processing:\t\t{length(network_subset.df$edge_id)}')
glue('Number of edges - post processing:\t\t{length(df$edge_id)}')
glue('Number of segments:\t\t\t\t{n_segments}')
glue('Number of intersections:\t\t\t{n_intersections}')
glue('Time Elapsed:\t\t\t\t\t{time_elapsed} seconds')
```

## Evaluate
#### Generate Linestring
```{r}
eval.sf <- makeLinestringVector(df)

eval.sf %>% glimpse()
```

#### Visually Inspect
```{r}
color_feature <- 'segment_id'
p <- plotStreets(eval.sf, color_feature)
plotly::ggplotly(p)
```

#### Data Inspect
```{r}
eval.sf %>% 
  filter(tiger.name_base == "Dinglewood")
```

# Multilinestring
## Concatenate linestrings
```{r}
test_segment_id <- "h3fmodqyw4"

ls_set <- eval.sf %>% 
  filter(segment_id == test_segment_id) %>% 
  pull(geometry)

ls_set
```

```{r}
# Convert to multistring
mls <- sf::st_multilinestring(ls_set) %>% 
  sf::st_sfc() %>% 
  st_set_crs(4326)

# Calculate multistring length
mls_len <- sf::st_length(mls)
mls_len
```

```{r}
# Segmentize
mls %>% 
  sf::st_segmentize(dfMaxLength = mls_len/100)
```

```{r}
sf::st_sfc(mls)

# Convert MULTILINESTRING to MULTIPOINT
mps <- sf::st_sfc(mls) %>% 
  sf::st_cast("POINT") %>% 
  st_set_crs(4326)

# Extract single line from set
l <- ls_set[2]
l

# Test Distance Function
## Multiline
dist_mls <- sf::st_is_within_distance(
  x = mls,
  y = l,
  dist = .05, 
  sparse = FALSE
)
dist_mls



## Multipoint
dist__mps <- sf::st_is_within_distance(
  x = mps,
  y = l,
  dist = .05, 
  sparse = FALSE
) 

dist_rate_mps <-   sum(dist__mps)/length(dist__mps)
dist_rate_mps
```



