---
title: "Exploration"
author: "Evan Canfield"
date: "7/30/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Purpose
Determine how to ensure roads represented as two parallel lines have the same segment intersections on both sides of the line.

# Import
## Packages
```{r import_packages}
if (!require(pacman)) {install.packages("pacman")}
pacman::p_load(
  glue,
  parallel,
  sf,
  stringi,
  tidyverse
)

# Import custom functions
r_files <- list.files("./../R/", full.names = TRUE)
for (file in r_files) {
  source(file)
}

# Set randomized seed
set.seed(5590)
```

## Data
### Street Map
```{r import_data}
# Street network data.frame
# Network has already been assigned segments, but has not be processed 
# to split parallel edges
network_raw.df <- readRDS("./../data/network_02_no_parallel_seperation_complete_2021-08-24.RDS")
```

# Subset
```{r subset_network}
SUBSET_NETWORK <- TRUE

if (SUBSET_NETWORK) {
  # Define subsetting Parameters
  center_lat <- 35.242974
  center_lon <- -80.794735
  radius     <- 1e3

  # Execute
  network.df <- subset_lat_lon(
    network    = network_raw.df, 
    lat_center = center_lat, 
    lon_center = center_lon,
    radius     = radius 
    )
  
} else{
  network.df <- network_raw.df
}

n_edge_sub <- length(network.df$edge_id)
n_edge_total <- length(network_raw.df$edge_id)
per_total <- round(100*(1 - ((n_edge_total - n_edge_sub)/n_edge_total)),1)

# Print output
print(glue::glue("Subset Network:\t\t{SUBSET_NETWORK}"))
if (SUBSET_NETWORK){
  print(glue::glue("Percent of Network:\t{per_total}%"))
}
```

# Consolidate Process
## Define Constants and Initial Values
```{r}
# Constants
## Radius
radius_m <- 10
safety_buffer <- 0.10
radius_adj <- radius_m * 2 * pi * (1 + safety_buffer)

## Angle
angle_buffer <- 0.015
```

## Define possible subsets
Input should be the node where there is a t intersection on one side of a parallel edge road.
```{r}
t_intersect_cases <- vector(mode = "list")
t_intersect_cases[['academy_at_the_plaza']] <- 5514326164
t_intersect_cases[['murdock_at_the_plaza']] <- 172383724
t_intersect_cases[['pickney_at_matheson']] <- 172250876
```

## Pre-process Data
```{r}
subset_tag <- FALSE
subset_label <- 'pickney_at_matheson'
subset_radius <- 100

# Subset
if (subset_tag) {
  # Reduce to subset node
  center_node.df <- network.df %>%
    filter(
      from_id == t_intersect_cases[[subset_label]]
      ) %>% 
  sample_n(size = 1)
  
  # Extract lat/lon
  subset_lon <- center_node.df %>% pull(from_lon)
  subset_lat <- center_node.df %>% pull(from_lat)
  
  # Subset
  network.df <- subset_lat_lon(
    network    = network.df, 
    lat_center = subset_lat, 
    lon_center = subset_lon, 
    radius     = subset_radius
    )
  }

# PROCESSING ##################################################################
# Calculate edge centerpoint
network.df <- network.df %>% 
  dplyr::mutate(
    center_lat = (to_lat + from_lat)/2,
    center_lon = (to_lon + from_lon)/2
  )

# Calculate edge angle to normal x,y axis. Angle is reported in units of pi 
# radians. Invert all negative angles.
network.df <- network.df %>% 
  dplyr::mutate(
    theta = atan2(
      y = to_lat - from_lat,
      x = to_lon - from_lon
      ) / pi ,
    theta = if_else(
      theta < 0, 
      theta + 1,
      theta
      )
  )

# Calculate angle of orthogonal projection to the edge. This is done by shifting
# the edge angle clockwise by by 1/2.
network.df <- network.df %>% 
  dplyr::mutate(
    theta_orth = theta + 1/2,
    theta_orth = if_else(
      theta_orth >= 2, 
      theta_orth - 2, 
      theta_orth
      )
  )

# Determine points of orthogonal projection. Because our data is representing
# a real world area, a 2D rendering is only a approximation. This affects the 
# implementation of length, which we need to determine the start and end 
# points of the orthogonal projection. Depending on the angle of the orthogonal 
# projection, length in the 2D space could be off by as much as a factor of 
# 2 PI. Therefore, in order for the length calculation to be conservative, we 
# will use a 2 PI factor to adjust the 2D length.

dist_adj_factor <- 2 * pi
dist_m = 15 
dist_adj <- dist_m * dist_adj_factor
m_to_deg = 111000
orth_deg <- dist_m/m_to_deg

network.df <- network.df %>% 
  dplyr::mutate(
    orth_x        = orth_deg * cos(theta_orth*pi),
    orth_y        = orth_deg * sin(theta_orth*pi),
    to_lat_orth   = (center_lat + orth_y),
    to_lon_orth   = (center_lon + orth_x),
    from_lat_orth = (center_lat - orth_y),
    from_lon_orth = (center_lon - orth_x),
  )

# Create Edge LINESTRING
network.sf <- makeLinestringVector(df = network.df, orthogonal = FALSE) %>% 
  select(ls_norm, everything())

# Determine Edge Length
network.sf <- network.sf %>% 
  dplyr::mutate(
    edge_length_m = as.vector(sf::st_length(ls_norm))
  )

# Initialize Parallel Process columns
network.sf <- network.sf %>% 
  dplyr::mutate(
    parallel_edges      = list(c("<EMPTY>")),
    parallel_segments   = list(c("<EMPTY>")),
    n_parallel_segments = -1,
  )

# Create Orthogonal Projection LINESTRINGs
network_orth.sf <- makeLinestringVector(
  df = network.df, 
  orthogonal = TRUE
  ) %>% 
  select(edge_id)
```

## Execute Loop
```{r}
start_time <- Sys.time()

# Define output print levels
## Time updates
print_flag_time <- TRUE
## Granular, step by step, print statements
print_flag_1 <- FALSE
## Parallel intersect checks
print_flag_2 <- FALSE

# Initial
while_check.sf <- network.sf %>% filter(n_parallel_segments == -1)
n_remaining <- length(while_check.sf$edge_id)
i <- 1

print(glue("Number of edges:\t\t\t{length(network.sf$edge_id)}"))

# Execute Loop
while (n_remaining > 0){
  
   # Runaway While Loop escape valve
  if(i %% 1e5 == 0) {
    break
  }
  
  # Time Updates
  if (verbose >= 1){
    if(i %% 5e2 == 0) {
      end_time <- Sys.time()
      time_elapsed <- secondsToPeriodTime(start_time, end_time)

      print(glue(paste0(rep(x = "_", 80), collapse = "")))
      print(glue('Iteration:\t\t\t\t{i}'))
      print(glue('Time Elapsed:\t\t\t\t{time_elapsed}'))
    }
  }
  
  # REDUCE DATASET BEFORE SHAPEFILE PROCESSES #################################
  # Setup ---------------------------------------------------------------------
  if (verbose >= 1){
    print(glue(paste0(rep(x = "_", 80), collapse = "")))
    print(glue('Iteration:\t\t\t\t{i}'))
  }
  
  # Establish dataframe variable
  # This reduces errors when the subsetting sequence is rearranged.
  network_subset.sf <- network.sf 
  
  # Select random row
  iter.df <- network_subset.sf %>% 
    filter(n_parallel_segments == -1) %>% 
    dplyr::slice_sample(n = 1)
  
  # Extract Inputs
  edge_id_iter    = iter.df %>% pull(edge_id)
  center_lat      = iter.df %>% pull(center_lat)
  center_lon      = iter.df %>% pull(center_lon)
  segment_id_iter = iter.df %>% pull(segment_id)
  theta_iter      = iter.df %>% pull(theta)
  
  if (print_flag_1){
    print(glue('Edge ID:\t\t\t\t{edge_id_iter}'))
    print(glue('Number of Edges - Total:\t\t{length(network.sf$edge_id)}'))
  }
  
  # Subset - Segment -----------------------------------------------------------
  network_subset.sf <- network_subset.sf %>% 
    filter(segment_id != segment_id_iter)  
  
  n_subset <- length(network_subset.sf$edge_id)
  
  if (print_flag_1){  
    print(glue('Number of Edges - Subset - Segment ID:\t{n_subset}'))
  }
  
  if (n_subset == 0) {
    network.sf <- exportParallelEdgeResults(
      network                    = network.sf, 
      input_edge_id              = edge_id_iter, 
      parallel_detected          = FALSE, 
      parallel_edges_detected    = NA, 
      parallel_segments_detected = NA
      )
    
    # Iteration  actions
    i <- i + 1
    while_check.sf <- network.sf %>% filter(n_parallel_segments == -1)
    n_remaining <- length(while_check.sf$edge_id)
    next
  }
  
  # Subset - Radius -----------------------------------------------------------
  network_subset.sf <- subset_lat_lon(
    network    = network_subset.sf, 
    lat_center = center_lat, 
    lon_center = center_lon,
    radius     = radius_adj 
    )
  
  n_subset <- length(network_subset.sf$edge_id)
  
  if (print_flag_1){
    print(glue('Number of Edges - Subset - Radius:\t{n_subset}'))
  }
  
  if (n_subset == 0) {
    network.sf <- exportParallelEdgeResults(
      network                    = network.sf, 
      input_edge_id              = edge_id_iter, 
      parallel_detected          = FALSE, 
      parallel_edges_detected    = NA, 
      parallel_segments_detected = NA
      )
     
    # Iteration  actions
    i <- i + 1
    while_check.sf <- network.sf %>% filter(n_parallel_segments == -1)
    n_remaining <- length(while_check.sf$edge_id)
    next
  }
  
  # Subset - Angle ------------------------------------------------------------
  ### Define max/min angle values
  theta_max <- theta_iter + angle_buffer
  theta_min <- theta_iter - angle_buffer
  
  ### Execute subset
  network_subset.sf <- network_subset.sf %>% 
    filter(
      between(
        x     = theta,
        left  = theta_min, 
        right = theta_max
        )
    )
  
  n_subset <- length(network_subset.sf$edge_id)
  
  if (print_flag_1){
    print(glue('Number of Edges - Subset - Angle:\t{n_subset}'))
  }
  
  if (n_subset == 0) {
    network.sf <- exportParallelEdgeResults(
      network                    = network.sf, 
      input_edge_id              = edge_id_iter, 
      parallel_detected          = FALSE, 
      parallel_edges_detected    = NA, 
      parallel_segments_detected = NA
      )
    
    # Iteration  actions
    i <- i + 1
    while_check.sf <- network.sf %>% filter(n_parallel_segments == -1)
    n_remaining <- length(while_check.sf$edge_id)
    next
  }
  
  # PARALLEL INTERSECTION CHECK ###############################################
  # Initialize
  parallel_edges_iter <- c()
  parallel_segments_iter <- c()
  
  for (comparison_edge_idx in seq_along(network_subset.sf$edge_id)){
    
    # Select orthogonal linestring to check intersection
    ls_orth <- network_orth.sf %>% 
      filter(edge_id == edge_id_iter) %>% 
      pull(ls_orth)
    
    # Select Row to compare
    row_comp <- network_subset.sf %>% slice(comparison_edge_idx)
    
    # Extract parameters for comparison  
    ls_comp         <- row_comp %>% pull(ls_norm)
    edge_id_comp    <- row_comp %>% pull(edge_id)
    segment_id_comp <- row_comp %>% pull(segment_id)
    
    # Check if the orthogonal projection and edge intersect
    ls_intersect <- sf::st_intersects(
      ls_orth, ls_comp, 
      sparse = FALSE
      )[[1]]
    
    how_close <- NA
    
    # Document edge and segment if they did intersect
    if (ls_intersect) {
      parallel_edges_iter    <- c(parallel_edges_iter, edge_id_comp)
      parallel_segments_iter <- c(parallel_segments_iter, segment_id_comp)
    
    } else {
      how_close <- sf::st_distance(ls_orth, ls_comp)
    }
    
    if (print_flag_2) {
      print(glue(paste0(rep(x = "-", 80), collapse = "")))
      print(glue("Edge ID:\t\t\t\t{edge_id_iter}"))
      print(glue("Edge ID - Comparison:\t\t\t{edge_id_comp}"))
      print(glue("Segment ID:\t\t\t\t{segment_id_iter}"))
      print(glue("Segment ID - Comparison:\t\t{segment_id_comp}"))
      print(glue("Intersect:\t\t\t\t{ls_intersect}"))
      
      if (!is.na(how_close)){
        print(glue("Distance:\t\t\t\t{how_close}"))
      }
      print(glue(paste0(rep(x = "-", 80), collapse = "")))
    }
    
  }
  
  # Check if any edges were found to be parallel
  if (length(parallel_segments_iter) > 0){
    
    network.sf <- exportParallelEdgeResults(
      network                    = network.sf, 
      input_edge_id              = edge_id_iter, 
      parallel_detected          = TRUE, 
      parallel_edges_detected    = parallel_edges_iter, 
      parallel_segments_detected = parallel_segments_iter
      )
    
  } else{
    
    network.sf <- exportParallelEdgeResults(
      network                    = network.sf, 
      input_edge_id              = edge_id_iter, 
      parallel_detected          = FALSE, 
      parallel_edges_detected    = NA, 
      parallel_segments_detected = NA
      )
    
  }
  
  # Iteration Actions
  while_check.sf <- network.sf %>% filter(n_parallel_segments == -1)
  n_remaining <- length(while_check.sf$edge_id)
  i <- i + 1
  next
}

end_time <- Sys.time()
time_elapsed <- secondsToPeriodTime(start_time, end_time)

print(glue(paste0(rep(x = "_", 80), collapse = "")))
print(glue('Time Elapsed - Final:\t\t\t{time_elapsed}'))
```

# Export
```{r}
file_dir <- "./../data/"
file_name <- "segmented_street_network_parallel_cases_labeled_10km.RDS"
file_path <- file.path(file_dir, file_name)
saveRDS(object = network.sf, file = file_path)
```

## Check Segments with Multiple Edges
```{r}
parallel_edge_pairs <- network.sf %>% 
  sf::st_drop_geometry() %>% 
  select(edge_id, segment_id, parallel_edges, parallel_segments) %>% 
  unnest(cols = parallel_segments) %>% 
  unnest(cols = parallel_edges) %>% 
  filter(parallel_segments != "<EMPTY>")
```

```{r}
# Table of all segments with parallel segments, long form
segment_breakdown <- network.sf %>% 
  sf::st_drop_geometry() %>% 
  select(edge_id, segment_id, parallel_segments, parallel_edges) %>% 
  unnest(cols = parallel_segments) %>% 
  unnest(cols = parallel_edges) %>% 
  filter(parallel_segments != "<EMPTY>") %>% 
  group_by(segment_id) %>%
  count(parallel_segments) %>% 
  ungroup() %>% 
  rename(
    parallel_segment = parallel_segments,
    n_parallel_edges = n
    ) %>% 
  arrange(segment_id, parallel_segment)

segment_breakdown %>% arrange(segment_id)
```

```{r}
# Summary table of the number of 
unique_parallel_segments <- segment_breakdown %>% 
  group_by(segment_id) %>%
  summarise(unique_parallel_segments = n()) %>%
  arrange(desc(unique_parallel_segments))

unique_parallel_segments
```

## Create Parallel Segment Pairs
### Wrap All Parallel Segments into List Column
```{r}
# Reduce to segments with two or more segment matches
parallel_segments.v <- unique_parallel_segments %>% 
  filter(unique_parallel_segments > 1) %>% 
  pull(segment_id)

parallel_segments.df <- segment_breakdown %>% 
  select(-n_parallel_edges) %>% 
  filter(segment_id %in% parallel_segments.v) %>% 
  group_by(segment_id) %>% 
  summarise(parallel_segments = list(unique(parallel_segment)))

parallel_segments.df %>% head(2)
```

### Scratch Work
```{r}
df_test <- x %>%
  filter(segment_id == "l0sztiy7lq")

df_test

long_id <- df_test %>% pull(segment_id)

short_segments <- df_test %>% pull(parallel_segments) %>% unlist()

short_segments

segment_sets.df <- as.data.frame(
  x = t(combn(short_segments, 2)) 
  ) %>% 
  mutate(long_segment = long_id) %>%
  rename(
    short_segment_1 = V1,
    short_segment_2 = V2
    ) %>% 
  select(long_segment, everything())


segment_sets.df
```

### Function - List All Possible Short Segment Pairs
```{r}
shortSegmentPairs <- function(segments.lst){
  as.data.frame(
    x = t(combn(unlist(segments.lst), 2)) 
  ) %>% 
  rename(
    short_segment_1 = V1,
    short_segment_2 = V2
    )
}

short_segments <- df_test %>% pull(parallel_segments)
```


## Visualize
Visually inspect what identified parallel segments look like.
```{r}
# Extract Segments to Highlight
long_segments <- unique_parallel_segments %>% 
  filter(unique_parallel_segments > 1) %>% 
  pull(segment_id)

short_segments_1 <- segment_breakdown %>% 
  filter(segment_id %in% long_segments) %>% 
  group_by(segment_id) %>% 
  mutate(row = row_number()) %>% 
  filter(row == 1) %>% 
  pull(parallel_segment)

short_segments_2 <- segment_breakdown %>% 
  filter(segment_id %in% long_segments) %>% 
  group_by(segment_id) %>% 
  mutate(row = row_number()) %>% 
  filter(row == 2) %>% 
  pull(parallel_segment)

# Create column for highlighting the plot
network.sf <- network.sf %>% 
  mutate(
    highlight = dplyr::case_when(
      segment_id %in% long_segments ~ "long", 
      segment_id %in% short_segments_1 ~ "short_1",
      segment_id %in% short_segments_2 ~ "short_2",
      TRUE ~ "default"
    )
  )

print(glue("Number of Cases: {length(long_segments)}"))

# Generate Plot
p <- plotStreets(network.sf, color_feature = "highlight")

# Apply color palette
color_pal <- c(
  "short_1" = "#E71D36", 
  "short_2" = "#FF9F1C",
  "long"    = "#2EC4B6", 
  "default" =  "#D6DBDF"
  )

p <- p + scale_colour_manual(values=color_pal)

# Generate interactive plot
plotly::ggplotly(p)
```

# Check if Short Parallel Segments Are Contiguous


# TO DO:
Consolidate to a list of parallel segment ids for each segment id
Check that if any list contains multiple
If multiple, are any of the group connected
If a segment id is parallel to two connected segment ids, then that segment id will be split
Split based on where an orthogonal projection at the shared point would intersect






