---
title: "Generate Intersection Nodes"
author: "Evan Canfield"
date: "7/30/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Purpose
Generate a simple features dataframe identifying the segments parallel to each edge id.

**Note**: This step is computationally taxing and takes longer than ideal. Therefore, this notebook has been set up to work while running on an AWS EC2 instance. An EC2 instance with a large number of virtual cores can be selected in order to speed up processing.

# Import
## Packages
```{r import_packages}
if (!require(pacman)) {install.packages("pacman")}
pacman::p_load(
  tidyverse
)

# Import custom functions
r_files <- list.files(
  path = "./../R/", pattern = "*.R", full.names = TRUE, 
  recursive = FALSE, include.dirs = FALSE
  )
for (file in r_files) {
  source(file)
}

# Set randomized seed
set.seed(5590)
```

## Data
### Street Map
```{r import_data}
AWS <- FALSE

input_file_name <- "network_02_no_parallel_seperation_complete_2021-08-24.RDS"

if (AWS) { 
  
  print(glue::glue("Load input from Google Drive location for AWS compatability."))
  
  file_url <- "https://drive.google.com/file/d/157YhnF-gN6LjYc535Rb7A74mPeE4Ws2n/view?usp=sharing"
  file_dir <- "./../data/googledrive_transfer/"
  file_path <- file.path(file_dir, input_file_name)
  
  google_drive_response <- googledrive::drive_download(
    file = googledrive::as_id(file_url), 
    path = input_file_path,
    overwrite = TRUE
    )
  
  file_path <- google_drive_response$local_path
  file_name <- google_drive_response$name

  } else {

  print(glue::glue("Load input locally."))

  # Define local file location
  file_dir <- "./../data"
  file_path <- file.path(file_dir, input_file_name)
  }

# Load file
network_raw.df <- readr::read_rds(file_path)
```

### Extract OSM Query Date
```{r extract_api_query_date}
date_regex <- "\\d{4}-\\d{2}-\\d{2}"
osm_query_date <- stringr::str_extract(file_name, date_regex)
print(osm_query_date)
```

# Subset
```{r subset_network}
SUBSET_NETWORK <- TRUE

if (SUBSET_NETWORK) {
  # Define subsetting Parameters
  center_lat <- 35.242974
  center_lon <- -80.794735
  radius     <- 5.7e2

  # Execute
  network.df <- subset_lat_lon(
    network    = network_raw.df, 
    lat_center = center_lat, 
    lon_center = center_lon,
    radius     = radius 
    )
  
} else{
  network.df <- network_raw.df
}

n_edge_sub <- length(network.df$edge_id)
n_edge_total <- length(network_raw.df$edge_id)
per_total <- round(100*(1 - ((n_edge_total - n_edge_sub)/n_edge_total)),1)

# Print output
print(glue::glue("Subset Network:\t\t{SUBSET_NETWORK}"))
if (SUBSET_NETWORK){
  print(glue::glue("Percent of Network:\t{per_total}%"))
}
```

# Label Parallel Segments for Each Edge ID
```{r label_parallel_segments}
network.df <- identifyParallelSegmentsPar(
  network    = network.df,
  k          = 7, 
  start_time = NA, 
  verbose    = 3
)

print(glue::glue("Segments labeled: {length(network.df$edge_id)}"))
```

# Export
```{r export}

output_file_name <- glue::glue("network_03_parallel_edges_identified_{osm_query_date}.RDS")

# Generate file path
file_dir <- "./../data"
output_file_path <- file.path(file_dir, output_file_name)

# Export file
readr::write_rds(
  x = network.df, 
  file = output_file_path
  )

print(glue::glue("{file_path}"))
AWS <- TRUE

if (AWS) {
  gdrive_file_dir <- "~/CoverEveryStreet/data_for_aws"
  gdrive_file_path <- file.path(gdrive_file_dir, output_file_name)
  
  googledrive::drive_upload(
    media = output_file_path, 
    path  = gdrive_file_path
    )
  
  print(glue::glue("File Exported to Google Drive."))
}

```

