---
title: "Network Subsetting"
author: "Evan Canfield"
date: "8/11/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Purpose
Test different methods for subsetting street networks based on different criteria. This testing will be used to develop methods and functions which will be used in the final product.

# Import
## Packages
```{r import_packages}
if (!require(pacman)) {install.packages("pacman")}
pacman::p_load(
  glue,
  microbenchmark,
  sf,
  stringi,
  tidyverse
)

# Import custom functions
r_files <- list.files("./../R/", full.names = TRUE)
for (file in r_files) {
  source(file)
}

# Set randomized seed
set.seed(5590)
```

## Data
### Street Map
```{r import_data}
# Street network data.frame
network_raw.df <- readRDS("./../data/dodgr_network_charlotte_nc_2021-03-17.RDS")

# Define column type to avoid messages
col_type <- c(
  "edge_id" = "character",
  "to_id" = "character",
  "from_id" = "character",
  "status" = "character"
)
```

# Processing
## Drop Duplicates
* There are duplicate rows, with from and to ids swapped
```{r}
# Record number of observations before dropping
n_edge_raw <- length(network_raw.df$edge_id)

# Drop duplicate observations
network.df <- network_raw.df %>% 
    mutate(
    dup_id = if_else(
      from_id > to_id, 
      paste(to_id, from_id, sep = "_"),
      paste(from_id, to_id,  sep = "_")
    )
  )  %>% 
  group_by(dup_id) %>% 
  filter(row_number()==1) %>% 
  ungroup() %>% 
  select(-dup_id)

# Record number of observations after dropping
n_edge_post <- length(network.df$edge_id)

glue('Number of observations - original:\t\t\t{n_edge_raw}')
glue('Number of observations - post duplicate removal:\t{n_edge_post}')
```

### Remove Street Types
```{r}
street_types <- c('path', 'primary_link', 'secondary_link', 'tertiary_link', 'trunk_link', 
                  'living_street')
network.df <- network.df %>% 
  filter(!(highway %in% street_types))
```

# Subset Street Network
## Reduce Network for Benchmarking
```{r}
network_n.df <- network.df %>% 
  sample_n(1000)

```


## Method 1: Geographical Location (Latitude / Longitude)
I will evaluate two different methods for subsetting by geographical location:
* Precise: Use geographic projections to calculate accurate location and distance values
* Approximate: Assume a 2D projection with a set value converting latitude/longitude distance into meters. 

The approximate method will not be as accurate, but I expect it to be far faster, and as the intent of this process is only to reduce the dataset to a general area, this trade-off is probably acceptable. But to ensure that it is, we will test both methods.

The approximation for converting latitude/longitude degrees to distance is from here:

[https://www.usna.edu/Users/oceano/pguth/md_help/html/approx_equivalents.htm](https://www.usna.edu/Users/oceano/pguth/md_help/html/approx_equivalents.htm)

### Global Parameters
```{r}
# Test location
test_lat <- 35.242974
test_lon <- -80.794735

# Degree to Meter Conversion (Approximation)
m_per_deg <- 111000 
```


### Precise - 3D Projection
#### Define Distance Function
```{r}
# Calculate the distance between two points by converting the points into
# a sf LINESTRING
line_dist_3d_m <- function(lat_1, lon_1, lat_2, lon_2, crs = 4326) {
  #` Convert two points to a line and calculate length, in meters
  sf::st_sfc(
    sf::st_linestring(
      rbind(
        c(lat_1, lon_1), 
        c(lat_2, lon_2)
        )
      ), 
    crs = crs
    ) %>% 
    sf::st_length() %>% 
    as.vector()
}
```


#### Define Subset Function Utilizing Distance Function
```{r}
# Subset Network
subet_geo_3d <- function(network, lat_1, lon_1, radius = 50, crs = 4326){
  network %>%
    mutate(
      dist_to = purrr::map2_dbl(
        to_lat, to_lon,
        ~line_dist_m(
          lat_1 = lat_1,
          lat_2 =.x,
          lon_1 = lon_1,
          lon_2 = .y,
          crs   = crs
          )
        ),
      dist_from = purrr::map2_dbl(
        from_lat, from_lon,
        ~line_dist_m(
          lat_1 = lat_1,
          lat_2 =.x,
          lon_1 = lon_1,
          lon_2 = .y,
          crs   = crs
          )
        )
    ) %>% 
  filter(
    (dist_to <= radius) | 
    (dist_from <= radius)
  )
  
}
```

#### Test
```{r}
subet_geo_3d(
  network = network_n.df,
  lat_1   = test_lat,
  lon_1   = test_lon,
  radius = 1000
  ) 
```

### Approximate - 2D Projection
#### Define Distance FUnction
```{r}
line_dist_2d_m <- function(lat_1, lon_1, lat_2, lon_2){
  # Calculate the length of the vector between points 1 and 2, assuming a 2D projection
  deg_lat <- abs(lat_2 - lat_1)
  deg_lon <- abs(lon_2 - lon_1)
  deg_vect <- sqrt(deg_lat^2 + deg_lon^2)
  
  # Convert degrees to meters
  deg_vect * m_per_deg
}
```

#### Define Subset
```{r}
# Subset Network
subet_geo_2d <- function(network, lat_1, lon_1, radius = 50, crs = 4326){
  network %>%
    mutate(
      dist_to = purrr::map2_dbl(
        to_lat, to_lon,
        ~line_dist_2d_m(
          lat_1 = lat_1,
          lat_2 =.x,
          lon_1 = lon_1,
          lon_2 = .y
          )
        ),
      dist_from = purrr::map2_dbl(
        from_lat, from_lon,
        ~line_dist_2d_m(
          lat_1 = lat_1,
          lat_2 =.x,
          lon_1 = lon_1,
          lon_2 = .y
          )
        )
    ) %>% 
  filter(
    (dist_to <= radius) | 
    (dist_from <= radius)
  )
  
}
```

#### Test
```{r}
subet_geo_2d(
  network = network_n.df,
  lat_1   = test_lat,
  lon_1   = test_lon,
  radius = 1000
  )
```

# Benchmark

Results: The 3D method is much slower, and the time it takes to complete increases exponentially with the amount of datapoints
```{r}
# # Select Dataset
# n = 1e3
# df <- network.df %>% 
#   sample_n(n)
# 
# # Define Radius
# radius = 1000
# 
# # Evaluate
# results <- microbenchmark::microbenchmark(
#   precise = subet_geo_3d(
#     network = df,
#     lat_1   = test_lat,
#     lon_1   = test_lon,
#     radius = radius
#     ),  
#   approximate = subet_geo_2d(
#       network = df,
#       lat_1   = test_lat,
#       lon_1   = test_lon,
#       radius = 1000
#       ),
#    times = 10
# )
```
